---
output:
  html_document: default
  pdf_document: default
---

---
title: "Rules & Tenure Models"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

TO DO:
-figure out how to run MCMC for the pval estimations...
- Set some global viz params to use for plots below.
-[Done 19-9-10]save all of the data import and wrangling to a separate script and export to an rdata file that we call back in here. 
-[Done 19-09-30]pull summary stats and cross-tabs to separate script.

```{r setup, echo = FALSE, message = FALSE, include = FALSE, warning= FALSE, cache= TRUE}
library(haven)  # this is the new package to use instead of (foreign)
#library(corrplot)
library(magrittr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(readxl)
library(knitr)
library(summarytools)
library(lme4)
library(sjPlot)
library(sjmisc)
library(stringr)
library(kableExtra)
library(qwraps2)

options(scipen = 999)


# This is pulled from teh vignette for the summarytools pkg, which gives
# these suggested specifications to enable easy viewing of outputs:
# https://cran.r-project.org/web/packages/summarytools/vignettes/Introduction.html

opts_chunk$set(results = 'asis',      # This is essential (can also be set #at the chunk-level)
                comment = NA, 
                prompt = FALSE, 
                cache = FALSE, # additional global settings I want to have for this doc:
                message = FALSE,
                warning = FALSE)

st_options(plain.ascii = FALSE,        # This is very handy in all Rmd documents
            style = "rmarkdown",        # This too
            footnote = NA,             # Avoids footnotes which would clutter the results
            subtitle.emphasis = FALSE  # This is a setting to experiment with - according tothe theme used, it might improve the headings layout
           )   

```

```{r, echo=FALSE, message=FALSE}
# this setting also also suggested from summarytools vignette:
st_css()                              # This is a must; without it, expect odd layout,
                                      # especially with dfSummary()

theme_set(theme_sjplot())
```


---- Data prep now located in 1_RTM-datapull.R: (hidden in report view)  
< not including Use params in the dataframe called td now >
That script does the following:
1. Everything is straight factors, num or chr except for Rules which is ordered.
2. Recodes household-level tenure vars:  
3. Per discussion on Jan 7 2018, have condensed use & possession responses in to one category. 
4. Adds dummy Vars for Rules : [this is only useful for a few of the models]
5. Creates a subset of the df that removes all records w/ NAs in Social capital

---- Data exploration and cross tabs now located in 2_RTM_dataexplore.R
 That script does the following:
1. basic cross tabs and chisq tests for assoc btwn model params


# Load Rdata files 
```{r}
load("./data/td.RData")
```


# MODELS:

In this doc I am only including the best models thus far. 
For full information on process of investigating alternate variable forms and model fits see Rules_model.Rmd

# 2. WINTER : 
Predicting Likelihood that a herder household will reserve Winter Pastures

## Formulas
We built {#} multilevel statistical models with different levels of complexity to model pasture managment behavior of herder households. In all models, the dependent variable was the binary variable of whether a household reserves Winter and Spring pastures. Model 1 is a random-intercept model without an explanatory variables. We included Organizational effects in the model as a random component; the assumption is that there is more similarity in the practices of a houshold within an organization that between organizations. In this model the variance iof the dependent variable is parsed in to household level variance and organization-level variance. 
*Eq. 1*: $y_{ij} = \gamma_{00} + U_{0j}$

where $y_i$ is the dependent variable measured at houhold $i$ in organization $j$. Model 1 was used as the baseline model to estimate the group-level variance in the dependent variable. We compared each model to an intercept-only model and models w random intercepts performed better in both instances.
We assessed subsets of the independent/predictor variables via a stepwise method to explore the relative model fits across different combinations of predictors.

*Eq. 2*: $y^*_{ij} = x_{ij}'\beta + u_i + \epsilon_{ij}$,

logit(Hipster) = B_1(Transport) +B_2(Irony) + B_0


### 2.1 Null Model & random effects
Determining support for specifying random effect for Organization. 
[We are going w Org, not Soum bc we have a hypothesis re: more var in herder practices between Orgs than within]

The estimate of the constant is the logit of the proportion Reserving Pastures:
Testing null models w just the randon intercept specified, to see which of these accounts for the most var. 
None of these models are significant in and of themselves, acording to straight p-vals, but by examining the AIC/BIC across the models we can see that for the Winter Pastures there is variation across Soum and Org (more variation between than within) and  
for the Spring Pastures there is more var across only Soums, not Org.  
But no support for random intercepts by ecological zone (jives with results from other model runs).

[Based on these I am going to just go w Org as grouping var (random) for both w & sp]
```{r}
nullw  <-  glm ( ResWint ~ 1 , data=td, family=binomial)   # AIC = 977
nullw.r <-  glmer( ResWint ~ 1 + (1|Org), data=td, family=binomial) #AIC = 947.2
nullw.re <-  glmer( ResWint ~ 1 + (1|ez), data=td, family=binomial) #worse
nullw.rs <-  glmer( ResWint ~ 1 + (1|Soum), data=td, family=binomial) #better
nullw.rso <-  glmer( ResWint ~ 1 + (1|Soum) + (1|Org), data=td, family=binomial)  #best, AIC = 934.4
nullw.rsxo <-  glmer( ResWint ~ 1 + (Org|Soum), data=td, family=binomial)  
#anova(nullw.r, nullw.re, nullw.rs, nullw.rso, nullw.rsxo)
print(anova(nullw.r, nullw.rs, nullw.rso)) 

nulls  <-  glm ( ResSpr ~ 1 , data = td, family = binomial)
nulls.r <-  glmer( ResSpr ~ 1 + (1|Org), data = td, family = binomial) #better  AIC = 950
nulls.re <-  glmer( ResSpr ~ 1 + (1|ez), data = td, family = binomial) #worse
nulls.rs <-  glmer( ResSpr ~ 1 + (1|Soum), data = td, family = binomial) #better  (best, AIC = 913)
nulls.rso <-  glmer( ResSpr ~ 1 + (1|Soum)+ (1|Org), data = td, family = binomial)  # AIC = 915
#anova(nulls.r, nulls.re, nulls.rs, nulls.rso)
anova(nulls.r, nulls.rs, nulls.rso)
anova(nulls.rso, nulls.rs, nulls.r)

```


```{r}
summary(nullw.r )
summary(nulls.r )
```
Ref: http://data.princeton.edu/wws509/R/c3s1.html  


###2.2 Winter Pasture Tenure & Rule Formality
** Household level tenure var:**
This model uses the response from the Household-level survey regarding whether the hh has a Use or Possession contract for the Winter Pasture. Also incorporated the hh-level Q regarding tenure status on the Winter **CAMPSITE** as a predictor for these models as well.
Compared  multiple models in original work (Rules_model.Rmd) with different combinations of Rule vars, cbrm status and Social Capital param. 

Also, ended up specifying random intercept for Org when using the hh-level Tenure var.
Is this signif bc there is Org-level influence on either a) what kind of tenure a hh woudl have and/or b) how much they actually know about their tenure-status?
(note: much worse fit if include a random intercept for ez when using hh level tenure var. surprising that this doesn't vary?)

Reserving Winter Pastures ~ Tenure + cbrm + Rules + SocCap + (1 | Org)

*Now Rules are more significant than cbrm status.*

[Note jan8: added ordinal Rule para rather than the dummy var Rule/No]
Below I have just the results of a stepwise model comparison, based on all of the previous work re: the rel of these params.
Stepwise:  [Can only do this with model without random intercepts included, but generally the same message if we compare these manually, which I do in a diff doc]
In general I don't want to use this, as it is not theory based, just throwing it all in, but we did lots of testing prior and this was just to check. 
```{r}
# DON:T USE THIS EXCEPT FOR BASIC EXPLORATION OF PARAMS.
fullmod <- glm(ResWint ~ hhTenureWCamp+hhTenureWPast +  Rule + RuleNo+ cbrmYN +cogSC1 +ez , family = binomial,data = td) 

fullmod <- glm(ResWint ~ hhTenureWCamp+hhTenureWPast +  Rule + RuleNo+ cbrmType +cogSC1  , family = binomial,data = td) 
backward <- step(fullmod)
summary(backward) #gives the best model


```

####Takeaway: The data are best explained by a model that includes:  
**Tenure on Winter Pasture AND Camp, Rule formality and cognitive social capital.**

BUT this form will not let us take random effects of Organization and/or Soum in to account, and we know from previous steps (see Rules_model.Rmd doc) that model fit improves with including random effect of Org, based on assumption that there may be more sim within group that among.  

So, this is the same model as above, but w random effects of Org specified. Modelling with BOTH winter tenure parameters :
Various attempts at models w ecological zone included as either fixed or random effect were not signif and/or performed poorly. Only ez3=Eastern Steppe was ever signif.

```{r}
# don't use this one bc Rules and CBRM are so correlated?? but it 
#htm7 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = td.sc)

htm7 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule +  cogSC1 +   (1|Org) , family = binomial, data = td.sc)   #AIC = 648
  # tested to see if interaction terms improved fit... 
  # shoudl we report this?
#htm7.2 <- glmer(ResWint ~ (hhTenureWPast + hhTenureWCamp + Rule +  cogSC1)^2 +   (1|Org) , family = binomial, data = td.sc)    # AIC = 649 
#htm7.4 <- glmer(ResWint ~ (hhTenureWPast + hhTenureWCamp + Rule +  cogSC1)^4 +   (1|Org) , family = binomial, data = td.sc) # AIC = 653

#anova(htm7, htm7.2, htm7.4, test = "Chisq")
summary(htm7)
  #analysis of deviance table:
car::Anova(htm7)
  # table of the odds ratios:
tab_model(htm7)

# Plot the estimates: 
  # plotting defaults to descending order with the highes effect at the top:
  #The “neutral” line, i.e. the vertical intercept that indicates no effect (x-axis position 1 for most glm’s and position 0 for most linear models), is   #drawn slightly thicker than the other grid lines. You can change the line color with the vline.color-argument.

plot_model(htm7, title = "Reserve Winter Pastures", auto.label = FALSE)


```
```{r}
wchi.diff<- (943.16-634.54)
wdf.diff<- (703-508)
pchisq(wchi.diff, wdf.diff, lower.tail = F)
```



**Can also look at the outputs as odds ratios:** which I find slightly easier to interpret.  
Based on htm7:

But, the Marginal R^2 is very low....
```{r}
tab_model(htm7)  # can add multiple to compare...
#tab_model(htm7, htm8)
```


The odds of a hh reserving winter pasture are lower if there are not Rules in place regarding timing of grazing of (winter pasture). 
However, the odds of the hh reserving pasture increase with increasing tenure on the winter camp. 
The odds of the household reserving pasture increases the most with increases in Social Capital.  
The conditional R2 describes the proportion of variance explained by both the fixed and random factors
morginal is just fixed factors.

But, while we can run the full models w random effect by Org specified and extract those coeffs (see above work) that **doesn't get us differences by ez which might be important,** and the models won't run w random effect by ez also included (won't converge)[this may be bc of issues revealed in the Steppe-only model  below?]
[Seeking help on this from another person]

So, maybe we look at these separately then. 
-either by ecological zone separately to see if diff models needed for diff zones. 
AND/or
-to assess the relative impacts of Rules across the zones. 

In the meantime, here's the original and predicted values. 
To visualize will have to decide a cut-off point for the fitted to assign 0/1
```{r}
df.htm7<- htm7@frame
wDat <- data.frame(htm7@frame, resid=residuals(htm7,type="pearson"),fitted=fitted(htm7))

theme= theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             panel.background = element_blank(),
             axis.text.y = element_blank(),
             axis.ticks = element_blank(),
             axis.line.x = element_line(color = "black"),
             axis.line.y = element_line(color = "black"),
             text = element_text(size = 20),
             legend.key = element_blank())
hist <- ggplot(wDat, aes(fitted, color = ResWint, fill = ResWint))
hist +
  theme +
  geom_dotplot(binwidth = 0.01, position = "jitter")+
  coord_cartesian(xlim = c(0,1))+
  xlab("Predicted value")+
  ylab(" ")+
  scale_color_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Winter Pastures")+
  scale_fill_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Winter Pastures")+
  geom_vline(xintercept = c(0.5), linetype = "dotdash", size = 1)

```

Let's explore the values w high predicted value but observed = 0 to see what's up. 
###Looks like there is a relationship between the level of social capital and the fitted value [where did i get that from? I don't see a huge diff in mean cogSC values] (pos). So operhaps the impact of SC1 is so great that the model is over prediction the probability that a hh will reserve pastures.###
```{r}
# filter the df of predicted vals it so it's the values on the right that were obsv No, pred Yes and look at summary stats:
#wDat%>%dplyr::filter(fitted >= 0.5) %>% filter(ResWint == 0) %>% summary_table(.)
badpred <- wDat%>%dplyr::filter(fitted >= 0.5) %>% filter(ResWint == 0)
# let's compare those to the summary stats for the correctly predicted:
#wDat%>%dplyr::filter(fitted >= 0.5) %>% filter(ResWint == 1) %>% summary_table(.)
goodpred <- wDat%>%dplyr::filter(fitted >= 0.5) %>% filter(ResWint == 1)


# merge w the original data so can visualize by EZ:

#wDat.td<- left_join(wDat, td, by = "Org")


#ggplot(badpred, aes(fitted))+geom_density()+theme_bw()

# histogram of predicted values, colored by Rule formality 
ggplot(badpred, aes(fitted, color= Rule)) + geom_density() 
# ggplot(wDat, aes(fitted, color= hhTenureWPast)) + geom_density() 
# ggplot(wDat, aes(fitted, color= hhTenureWCamp)) + geom_density() 
# ggplot(wDat, aes(fitted, color= ResWint)) + geom_density() 
```


# 3. Reserve Spring Pastures**  

Do we see similar relationships with potential explanatory variables?  
nullSp<- glm( ResSpr ~1, data= td, family = binomial)  
This only works when we use the dummary variable version of the Rules var: RuleNo or RuleInf both work w basically same result. 
Again, not using the Org-level tenure var anymore.
```{r}
 ## Sp Pasture, household level tenure var:
htmSp <- glmer(ResSpr ~ hhTenureSpPast + cbrmYN + RuleNo + cogSC1 + (1|Org) , family = binomial, data = td ) # hmmmm.... now cbrm signif
summary(htmSp)

```

Double checking model fit with a stepwise procedure confirms (without the random effects) the significance of:  
**Household tenure on the Spring Pasture, *cbrm status* and cognitive social capital.** 
```{r}
fullSpmod <- glm(ResSpr ~ hhTenureSpPast+ hhTenureSpCamp+ Rule + RuleNo+ cbrmYN +cogSC1 , family = binomial,data = td.sc) 
backward <- step(fullSpmod)
#summary(backward) #gives the best model
```

Best model as determined above, with the random effect of Org, presented as odds ratios:
```{r}
bestSp <- glmer(formula = ResSpr ~ hhTenureSpPast + hhTenureSpCamp+ cbrmYN + RuleNo+ cogSC1 + (1|Org), family = binomial, 
    data = td)
summary(bestSp)
tab_model(bestSp)

coef(summary(bestSp))

plot_model(bestSp,
           title = "Reserve Spring Pastures", 
           sort.est = TRUE,
           #auto.label = FALSE, 
           axis.labels = c("Rules","cbrmYN","Camp Tenure", "Social Capital", "Pasture Tenure"),
           colors = "blue") 
```

```{r}
# visualizing the varation in intercepts across the Orgs.

int<- bestSp@beta
Spint<- int[1]
# explore the variation in intercepts across Orgs:
org<- coef(bestSp)
Sorg<- org$Org 
# Rename a column in R
colnames(Sorg)[colnames(Sorg)=="(Intercept)"] <- "Int"


ggplot(Sorg, aes(x= (Int))) + geom_density() + geom_vline(xintercept = Spint)


```

**Interpretting the odds ratios:**  tenure on the spring pasture, membership in a formal CBRM and cognitive social capital all increase the odds that a household will reserve the spring pastures. Rules (re: timing of grazing) were not significant, but the coeffs indicate that the negative impact of NOT having rules on the odds of reserving pasture.. Conditional R2 describes the proportion of variance explained by both the fixed and random factors ... which, doesn't seem great?


In the meantime, here's the original and predicted values. 
To visualize will have to decide a cut-off point for the fitted to assign 0/1
```{r}
df.bestSp<- bestSp@frame
spDat <- data.frame(bestSp@frame, resid=residuals(bestSp,type="pearson"),fitted=fitted(bestSp))

theme= theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             panel.background = element_blank(),
             axis.text.y = element_blank(),
             axis.ticks = element_blank(),
             axis.line.x = element_line(color = "black"),
             axis.line.y = element_line(color = "black"),
             text = element_text(size = 20),
             legend.key = element_blank())
hist = ggplot(spDat, aes(fitted, color = ResSpr, fill = ResSpr))
hist +
  theme +
  geom_dotplot(binwidth = 0.01, position = "jitter")+
  coord_cartesian(xlim = c(0,1))+
  xlab("fitted value for probability reserve patures")+
  ylab(" ")+
  scale_color_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  scale_fill_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  geom_vline(xintercept = c(0.5), linetype = "dotdash", size = 1)


ggplot(spDat, aes(fitted, color= ResSpr)) + geom_density() +
  scale_color_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  scale_fill_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  geom_vline(data= filter(spDat, ResSpr == 1), aes(xintercept=median(fitted, na.rm=T)),  
               color="#2C3539", linetype="dashed", size=1)+
  geom_vline(data= filter(spDat, ResSpr == 0), aes(xintercept=median(fitted, na.rm=T)),  
               color="Maroon", linetype="dashed", size=1)+
  theme

```

```{r}

# histogram of predicted values, colored by Rule formality 
ggplot(spDat, aes(fitted, color= RuleNo)) + geom_density() 
ggplot(spDat, aes(fitted, color= hhTenureSpPast)) + geom_density() 
ggplot(spDat, aes(fitted, color= cbrmYN)) + geom_density() 

# boxplot of fitted values by Rule and hh Tenure on W Pasture
f<- ggplot(wDat, aes(x=Rule, y = fitted))
f+ geom_boxplot() +
  theme_bw() +
  xlab("Rule formality")+
  ylab("predicted probability reserve patures") +
  facet_grid(.~hhTenureWPast) 
  

```





### SOCIAL CAPITAL & RULES ...  

Given what we see above wrt the (weak) relationship between (this particular set of) Rules and (this one) Practice, does this mean for our hypothesized relationships between Social Capital and the prevalance of Informal vs. Formal Rules? Does it vary by TYPE of pasture/season under consideration? Stronger relationship between rule formality and social capital for the Winter pastures compared to Spring pastures.

**Original Hypothesis:**  
  Increased cognitive social capital will lead to more prevalence of *informal* rules (within certain ecological zones)
  Rules ~ Social Capital + ecological zone

But is there a chance that we have the order/direction of causality wrong in that?
  It could be Soc Cap ~ Rules + ez
    - or -
  Soc Cap ~ Rules + (1|ez)  NO. More likely Rule as a results of SC not other way around.
  
#### SC1 
```{r, message = FALSE, warning= FALSE}
library(MASS)
# need to use MASS::polr for ordered logistic regression
rezm<- polr(Rule ~ ez, data = td, method = c("logistic"))
rscm<- polr(Rule ~ cogSC1 , data = td, method = c("logistic"))
rse1<- polr(Rule ~ cogSC1 + ez, data = td, method = c("logistic"))
anova(rezm, rscm) # big improvement by including ez, as we predicted
summary(rse1) # outputs are re: prob of being in that class or lower
#intercepts are the zetas


#  Tenure as predicted by Rule formality and EZ
rtez<- glm(hhTenureWPast ~ Rule + ez +cogSC1, data= td, family = "binomial")
summary(rtez)
# :
rtez_dat <- cbind(expand.grid(Rule=c(0,1,2),  ez = rep(1:4, 100), cogSC1=seq(0,2, 0.25))) #hhTenureWPast= c(0,1),
rtez_dat <- cbind(expand.grid(Rule=c(0,1,2),  ez = rep(1:4), cogSC1=seq(0,2, 0.25))) #hhTenureWPast= c(0,1),

# start w just one value for each
#fo_dat <- cbind(expand.grid(otherPast=c(1,2,3),Rule=c(0,1,2), hhTenureWPast= c(0,1), cogSC1=seq(0,2, 0.25)))

rtez_dat %<>% mutate_at(1, funs(ordered(.)))
rtez_dat %<>% mutate_at(c(2), funs(factor(.)))

rtezPred <- predict(rtez, rtez_dat, type="response")
rtezpredDat <- data.frame(rtez_dat, rtezPred)

#rnewdat<- cbind(rtez_dat, predict(rtez, rtez_dat, type = "response"))
# this doesn't work bc not ordered response....
#rtnewdat <- data.table::melt(rnewdat, id.vars = c("cogSC1", "ez"),
 #                variable.name = "Rule_Level", value.name = "Probability")


# scm<- lm(cogSC1 ~ ez, data =td, method = c("logistic"))
# scm1<- lm(cogSC1 ~ Rule, data =td, method = c("logistic"))
# anova(scm, scm1)
# scm<- glmer(cogSC1 ~ Rule + (1|ez), data =td)
# summary(scm)

# FITTED VALS:
fit.rse<- rse1$fitted.values
colnames(fit.rse)<- c("None", "Informal", "Formal")
rse.df<- data.frame(fit.rse, rse1$model)

# rse_dat <- data.frame(cogSC1 = seq(0, 2, length.out= 200), ez = rep(1:4, 50))
# rse_dat <- cbind(expand.grid(ez = seq(1,4, 1), cogSC1 = seq(0, 2, 0.1)))
# 
# rse_dat$ez<- as.factor(rse_dat$ez)
# newdat<- cbind(rse_dat, predict(rse1, rse_dat, type = "probs"))
# 
# 
# lnewdat <- melt(newdat, id.vars = c("cogSC1", "ez"),
#                 variable.name = "Rule_Level", value.name = "Probability")

rse.df<- gather(rse.df, "Level", "PredProb", 1:3)

ggplot(rse.df, aes(x= cogSC1, y=PredProb, color= Level )) +
  #geom_smooth()+  
  geom_line()+
  #geom_smooth(position=position_jitter(width=.01,height=.01))+
  coord_cartesian(xlim = c(0,2), ylim = c(0,0.75))+
  xlab("Cognitive Social Capital")+
  ylab("Pred Prob of Class Membership") +
  facet_grid(Rule~ez, labeller = label_both)


ggplot(lnewdat, aes(x= cogSC1, y= Probability, color = Rule_Level))+
  geom_smooth()+
    facet_grid(.~ez)+
  # coord_cartesian(xlim = c(0,2), ylim = c(0,0.75))+
  xlab("Cognitive Social Capital")+
  ylab("Pred Prob of Class Membership") 

ggplot(rtezpredDat, aes(x= cogSC1, y= rtezPred, color = Rule))+
  geom_smooth()+
  facet_grid(.~ez)+
   #coord_cartesian(xlim = c(0,2), ylim = c(0,0.75))+
  xlab("Cognitive Social Capital")+
  ylab("Pred Prob of Class Membership") 


ggplot(rtezpredDat, aes(x= rtezPred, y= cogSC1))+
  geom_bin2d()+
  facet_grid(ez~Rule)+
   #coord_cartesian(xlim = c(0,2), ylim = c(0,0.75))+
  xlab("Cognitive Social Capital")+
  ylab("Pred Prob of Class Membership") 
```

Big improvement by including ez, as we predicted

# returns predicted class membership, so look for the highest estimated probability in each zone.
Edit this to create a table:
```{r}
# EZ = 1
predict(rse1, newdata = data.frame(ez="1"),type="p") #0 = No rules, Inf next
# EZ = 2
predict(ezm, newdata = data.frame(ez="2"),type="p") #1 = Inf, formal next
#EZ = 3
predict(ezm, newdata = data.frame(ez="3"),type="p") #1 = Inf, then no, then formal
#EZ = 4
predict(ezm, newdata = data.frame(ez="4"),type="p") #1 = Inf, then formal next


# calc cumulative probabilities of having certain rule formality:
exp(ezm$zeta - ezm$coefficients)/(1 + exp(ezm$zeta - ezm$coefficients))

# how would this apply w a 
exp(rse1$zeta - rse1$coefficients)/(1 + exp(rse1$zeta - rse1$coefficients))


#ggplot(scm.df, aes(x=)) 
```








**Separating out the data by ecological zone** 
to try to understand why having issues trying to incorporate ez:  
td by ez
```{r}
mfs <- td %>% filter(ez == 4)%>% drop_na()
ds  <- td.sc %>% filter(ez == 1)%>% drop_na()
st  <- td.sc %>% filter(ez == 2) %>% drop_na()

```
Now separate models for each ez

1st: Rules by EZ:
```{r}
# singular fit warning, but does yield diff coefficients for Rules by ez....
mtez<- glmer(ResWint ~ Rule + (1+ Rule|ez), family = binomial,data = td) 
coef(mtez)
```
Now separate models for each ez... based on the full models above:
htm7 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = td.sc)
htmSp <- glmer(ResSpr ~ hhTenureSpPast + cbrmYN + RuleNo + cogSC1 + (1|Org) , family = binomial, data = td ) 

**This isn't working out**  
So i'm hiding it for now.
None fitting? Intercept only models best for DS and ST?  
And social capital the only signif param in FMS? 
```{r, echo = FALSE, eval = FALSE}
mt.null <-  glm( ResWint ~ 1, data=mfs, family=binomial)
ds.null <-  glm( ResWint ~ 1, data=ds, family=binomial)
st.null <-  glm( ResWint ~ 1, data=st, family=binomial)

  # this model will not converge unless all of these parameters are included??
#mtm <- glmer(ResWint ~ TenureWPast + Rule + cbrmYN + cogSC1 + (1|Org) , data = mfs, family = "binomial")

mtmp <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = mfs)
stmp <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = st)
dsmp <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = ds)


#dsmp <- glm(ResWint ~  hhTenureWPast+ hhTenureWCamp + Rule + cogSC1 , data = ds, family = "binomial")
dsfull <- glm(ResWint ~  hhTenureWPast+ hhTenureWCamp + cbrmYN+ Rule + cogSC1 , data = st, family = "binomial")
step(dsfull)
  # NONE OF THIS IS SIGNIF???
stfull <- glm(ResWint ~  hhTenureWPast+ hhTenureWCamp + cbrmYN+ RuleNo + cogSC1 , data = st, family = "binomial")
back<- step(stfull)

```


more histograms of params divided out by EZ:
```{r}
ggplot(ds, aes(cogSC1))+geom_density()+facet_grid(.~Rule)
ggplot(mfs, aes(cogSC1))+geom_density()+facet_grid(.~Rule)
ggplot(st, aes(cogSC1))+geom_density()+facet_grid(.~Rule)
ggplot(td, aes(cogSC1))+geom_density()+facet_wrap(.~Rule*ez)+theme_bw()

```



## ALSO NEED TO LOOK AT PREDICTED VALUES/DISTRIBUTIONS:
Our goal here is to calculate a predicted probability of Reserving Winter Pastures, for specific values of the predictors:
Tenure = 1
Rules = 1 vs. 2
cogSC1 continuous values….
To do that, create a dataframe w the specified values:
But we'll need to consider all combinations in order to really predict.

```{r}

      ##### THESE ARE NOT RUN W THE RANDOM INTERCEPT ####

finalW <- glm(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cogSC1, family = binomial, data = td)


finalWfg<- 

# start w just one value for each
p_dat <- cbind(expand.grid(hhTenureWPast=c(0,1),hhTenureWCamp=c(0,1),Rule=c(0,1,2), cogSC1=seq(0,2, .25)))

p_dat %<>% mutate_at(c(1:2), funs(factor(.)))
p_dat %<>% mutate_at(3, funs(ordered(.)))





#predict(finalW, p_dat, type="response")
wPred<- predict(finalW, p_dat, type="response")

predDat <- data.frame(p_dat, wPred)


twp<- ggplot(predDat, aes(x= wPred, y=hhTenureWPast))+
  geom_dotplot(binaxis = "y", stackdir = "center")+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Winter Pasture ")
twp

twp<- ggplot(predDat, aes(x= wPred, color=hhTenureWPast))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Winter Pasture ")
twp

twc<- ggplot(predDat, aes(x= wPred, color=hhTenureWCamp))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Winter Camp ")

rf<- ggplot(predDat, aes(x= wPred, color=Rule))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Rule formality ")+
    #geom_vline(data= filter(predDat, Rule == 1), aes(xintercept=median(fitted, na.rm=T)),  
      #         color="#2C3539", linetype="dashed", size=1)+
  geom_vline(data= filter(predDat, Rule == 1), aes(xintercept=median(wPred, na.rm=T)) ,  
               color="#2C3539", linetype="dashed", size=1)+
  geom_vline(data= filter(predDat, Rule == 0), aes(xintercept=median(wPred, na.rm=T)),  
               color="Maroon", linetype="dashed", size=1)
rf


ggplot(predDat, aes(x= cogSC1, y= wPred, color = Rule))+
  geom_smooth()+
  coord_cartesian(xlim = c(0,2))+
  xlab("cognitive social capital")+
  ylab("predicted prob of reserving W pasture") +
  facet_wrap(.~hhTenureWPast)

ggplot(predDat, aes(x= wPred, y= hhTenureWPast, color = Rule))+
    geom_point(shape=1,position=position_jitter(width=.1,height=.1))

ggplot(predDat, aes(x= wPred, y= hhTenureWCamp, color = Rule))+
    geom_point(shape=1,position=position_jitter(width=.1,height=.1))

ggplot(td, aes(x= cogSC1, y= Rule))+
    geom_point(shape=1,position=position_jitter(width=.1,height=.1))+
    facet_wrap(.~ez)

```

Looking more at the predicted values:

```{r}
predDat%>%group_by(hhTenureWPast)%>%
  summarise(pred= median(wPred))

predDat%>%group_by(hhTenureWCamp)%>%
  summarise(pred= median(wPred))

predDat%>%group_by(Rule)%>%
  summarise(pred= median(wPred))


```

THESE DON"T INCLUDE THE RANDOM EFFECT>>>>>
```{r}
finalS <- glm(ResSpr ~ hhTenureSpCamp + hhTenureSpPasture +cbrmYN + RuleNo + cogSC1, family = binomial, data = td)

# start w just one value for each
sp_dat <- cbind(expand.grid(hhTenureSpCamp=c(0,1),cbrmYN=c(0,1),Rule=c(0,1,2), cogSC1=seq(0,2, .25)))

sp_dat %<>% mutate_at(c(1:2), funs(factor(.)))
sp_dat %<>% mutate_at(3, funs(ordered(.)))





#predict(finalW, p_dat, type="response")
sPred<- predict(finalS, sp_dat, type="response")

spredDat <- data.frame(sp_dat, sPred)


ggplot(spredDat, aes(x= sPred, y=hhTenureSpCamp))+
  geom_dotplot(binaxis = "y", stackdir = "center")+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Spring Pasture ")


ggplot(spredDat, aes(x= sPred, color=hhTenureSpCamp))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Spring Pasture ")


ggplot(spredDat, aes(x= sPred, color=Rule))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Rule formality ")

ggplot(spredDat, aes(x= cogSC1, y= sPred, color = Rule))+
  geom_smooth()+  
  #geom_smooth(position=position_jitter(width=.01,height=.01))+
  coord_cartesian(xlim = c(0,2))+
  xlab("cognitive social capital")+
  ylab("predicted prob of reserving Sp pasture") +
  facet_wrap(.~hhTenureSpCamp)

ggplot(spredDat, aes(x= sPred, y= hhTenureSpCamp, color = Rule))+
    geom_point(shape=1,position=position_jitter(width=.1,height=.1))


```

Looking more at the predicted values:

```{r}
spredDat%>%group_by(hhTenureSpPast)%>%
  summarise(pred= median(sPred))

spredDat%>%group_by(hhTenureSpCamp)%>%
  summarise(pred= median(sPred))

spredDat%>%group_by(Rule)%>%
  summarise(pred= median(sPred))


```

NOT USEFUL YET
```{r, eval = FALSE}
theme= theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             panel.background = element_blank(),
             axis.text.y = element_blank(),
             axis.ticks = element_blank(),
             axis.line.x = element_line(color = "black"),
             axis.line.y = element_line(color = "black"),
             text = element_text(size = 20),
             legend.key = element_blank())
hist<- ggplot(predDat, aes(x= wPred, y= hhTenureWPast)) # color = ResWint, fill = ResWint))
hist +
  theme +
  #geom_dotplot(binwidth = 0.01, position = "jitter")+
  geom_dotplot(binaxis = "y")+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Winter Pasture ")+
  scale_color_manual(values = c("DkBlue", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  scale_fill_manual(values = c("DkBlue", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Winter Pastures")+
  geom_vline(xintercept = c(0.5), linetype = "dotdash", size = 1)




r.betas<- ggplot(mz.or, aes(x= ez, y = beta))+ 
  geom_point(size = 2)+
  theme+
   coord_cartesian(ylim = c(0,2))

kable(mz.or, format = "markdown")
```










# Create a new dataframe that includes population of people and livestock (as of now just aimag level #s, but woudl be interesting to look at soum level too)

```{r, eval = FALSE}
pop<- read.csv("./data/mor2data/2009Population.csv", header = TRUE)
# human population in thousands
# lsk population in thousands 

td$Aimag<- str_trim(td$Aimag, side = "both")

pop %<>% dplyr::select(-aimag)

#paused 
#td.a <- left_join(td, pop, by = c("Aimag"))
#td.a<- td.a %>% drop_na()
```

# FORAGE USE
11/26:Forage use is a highly significant parameter in the Winter model, but there doesn't seem to be much var in values between Res Wtr and No....and the effect size is low.

12/1: 1. Whiel I though tit made sense to use Soum as the RE here, actually that performs much more poorly, and get way better model fit if continue to use Org as the RE parameter.
2. What is the most appropriate way to indicate that forage use params are the same for all hh within the same Soum? It's a Soum-level var rather than a hh-level one.
```{r}
#WINTER:

# To load the dataframe that has frg use in it:
load("./data/tdfg.RData")
# switching the direction of forage use:
  # so that the results can be interpretted a little more easily:
td.fg %<>% mutate(frg.left =(100-frgUse))
td.fg<- rename(td.fg, frg.avg = frgUse, frg.cv = CV)


# Deprecatred bc Soum not useful RE:
  #wfm<- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule +  cogSC1 + frg.left+   (1|Soum) , family = binomial, data = td.fg)  

  #BEST:
wfm0<- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule +  cogSC1 + frg.left+   (1|Org) , family = binomial, data = td.fg)  

wfm2<- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule +  cogSC1 + frg.left+  frg.cv+ (1|Org) , family = binomial, data = td.fg) 

wm<- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule +  cogSC1 +    (1|Org) , family = binomial, data = td.fg)  

#wfm<- glmer(ResWint ~ hhTenureWCamp + Rule +  cogSC1 + frg.left+   (1|Org) , family = binomial, data = td.fg) 

tab_model(wm,wfm2, wfm0,   show.aic = TRUE)
# wm<- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule +  cogSC1 +    (1|Org) , family = binomial, data = td)  

#  Nesting frg.avg within Soum:
# wfm<- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule +  cogSC1 + (1|Soum) + (Soum:frg.avg) , family = binomial, data = td.fg)  

# start w just one value for each
p_dat <- cbind(expand.grid(hhTenureWPast=c(0,1),
                           hhTenureWCamp=c(0,1),
                           #otherPast = c(1,2,3),
                           Rule=c(0,1,2), 
                           cogSC1=seq(0,2, .1),
                           frg.left = seq(0,100,1),
                           frg.cv = seq(0,100,1)
                           ))


p_dat %<>% mutate_at(c(1:2), funs(factor(.)))
p_dat %<>% mutate_at(3:4, funs(ordered(.)))

# remove the RE for prediction 
wfmod<- glm(ResWint ~ hhTenureWPast+hhTenureWCamp +otherPast+Rule +cogSC1 +frg.left +frg.cv,
            family = binomial, 
            data = td.fg)  
#predict(finalW, p_dat, type="response")
wfPred<- predict(wfmod, p_dat, type="response")
predwfDat <- data.frame(p_dat, wfPred)

ggplot(td.fg, aes(x= frg.avg, color = ResWint))+geom_density()
ggplot(td.fg, aes(x= frg.avg))+geom_histogram()


# grid by Tenure
ggplot(predwfDat, aes(x= cogSC1, y = wfPred, color = Rule))+
  geom_smooth()+
  coord_cartesian(xlim = c(0,2), ylim = c(0,1))+
  xlab("cognitive social capital")+
  ylab("predicted prob of reserving winter pasture") +
  facet_grid(.~hhTenureWPast, labeller = label_both)

```


```{r}
# deprecated bc the other models have better fit w Org param for RE, and for Spring there isn't a huge diff between them, so sticking w Org:
#sfm<- glmer(ResSpr ~ hhTenureSpPast + hhTenureSpCamp + Rule + cogSC1 +frg.left + frg.cv + (1|Soum), family = binomial, data = td.fg)

sfm0<- glmer(ResSpr ~ hhTenureSpPast + hhTenureSpCamp + RuleNo + cogSC1 +frg.left + frg.cv + (1|Org), family = binomial, data = td.fg)

sfm1<- glmer(ResSpr ~ hhTenureSpPast + hhTenureSpCamp + RuleNo + cogSC1 +frg.left  + (1|Org), family = binomial, data = td.fg)

sfm2<- glmer(ResSpr ~ hhTenureSpPast + hhTenureSpCamp + RuleNo + cogSC1 +frg.cv +  (1|Org), family = binomial, data = td.fg)

sm<- glmer(ResSpr ~ hhTenureSpPast + hhTenureSpCamp + RuleNo + cogSC1 + (1|Org), family = binomial, data = td.fg)

sfm3<- glmer(ResSpr ~ hhTenureSpPast + hhTenureSpCamp + cogSC1+ frg.left + frg.cv  + (1|Org), family = binomial, data = td.fg)

# sfm3.1<- glmer(ResSpr ~ hhTenureSpCamp + cogSC1+ frg.left + frg.cv  + (1|Org), family = binomial, data = td.fg)

tab_model(sfm0,sfm1, sfm2, sfm3, show.aic = TRUE)

tab_model(sfm1, sm, show.aic = TRUE)

ggplot(td.fg, aes(x= frg.left, color = ResSpr))+geom_density(na.rm = TRUE)

# remove the RE for prediction 
# start w just one value for each
sp_dat <- cbind(expand.grid(hhTenureSpPast=c(0,1),
                           hhTenureSpCamp=c(0,1),
                          # otherPast = c(1,2,3),
                           RuleNo=c(0,1), 
                           cogSC1=seq(0,2, .1),
                           frg.left = seq(0,100,1),
                           frg.cv = seq(0,100,1)
                           ))


sp_dat %<>% mutate_at(c(1:2), funs(factor(.)))
sp_dat %<>% mutate_at(3:4, funs(ordered(.)))

sfmod<- glm(ResSpr~ hhTenureSpPast + hhTenureSpCamp + RuleNo + cogSC1 +frg.left + frg.cv,
            family = binomial, 
            data = td.fg)  
#predict(finalW, p_dat, type="response")
sfPred<- predict(sfmod, sp_dat, type="response")
predsfDat <- data.frame(sp_dat, sfPred)


# grid by Tenure
ggplot(predsfDat, aes(x= cogSC1, y = sfPred, color = RuleNo))+
  geom_smooth()+
  coord_cartesian(xlim = c(0,2), ylim = c(0,1))+
  xlab("cognitive social capital")+
  ylab("predicted prob of reserving spring pasture") +
  facet_grid(.~hhTenureSpPast, labeller = label_both)

```

#Otor x forage -- 
  Note: for this as well it seems that using Org as the RE results in better fit to data than Soum as RE.
For this as well it appears that going on otor is related to having access and also forage used... but why is THIS one negative? I would think that going on otor would be infl by having low availab resources.... but it seems to neg afect it? 
```{r}
#wofg <- glmer(Wotor ~  otherPast + Rule +  cogSC1 +frg.left+   (1|Soum), family = binomial, data = td.fg) 
# wofg1 <- glmer(Wotor ~  otherPast + Rule +  bondSC +frg.avg+   (1|Soum), family = binomial, data = td.fg) 
  # BEST:

wofg  <- glmer(Wotor ~  otherPast +   (1|Org), 
               family = binomial, 
               data = td.fg) 
wofg1 <- glmer(Wotor ~  otherPast + frg.left+   (1|Org), 
               family = binomial, 
               data = td.fg) 
wofg2 <- glmer(Wotor ~  otherPast + frg.cv+ (1|Org), 
               family = binomial, 
               data = td.fg)

wofg3 <- glmer(Wotor ~  otherPast + frg.left + frg.cv+ (1|Org), 
               family = binomial, 
               data = td.fg)
wofg4 <- glmer(Wotor ~  otherPast +frg.left+   Rule + cogSC1 + (1|Org), 
               family = binomial, 
               data = td.fg) 
# wofg01 <- glmer(Wotor ~ otherPast +Rule + cogSC1 + frg.left+  frg.cv+ (1|Org),
#                 family = binomial, 
#                 data = td.fg) 

   # Use this one for the prediction figure below, bc it includes Rules:
wofr <- glmer(Wotor ~  otherPast +Rule  + frg.left+  (1|Org), 
              family = binomial, data = td.fg) 


tab_model( wofg, wofg1, wofg2, wofg3,wofg4, show.aic = TRUE)

  # Best
fotor <-glmer(Fotor ~  otherPast + Rule +  cogSC1 + frg.avg+ frg.cv+  (1|Org),
              family = binomial, 
              data = td.fg)
  # no different, so using for 


fotor <-glmer(Fotor ~  otherPast +  (1|Org),
              family = binomial, 
              data = td.fg)
fotor1 <-glmer(Fotor ~  otherPast +  frg.left+  (1|Org),
              family = binomial, 
              data = td.fg)
fotor2 <-glmer(Fotor ~  otherPast + frg.cv+  (1|Org),
              family = binomial, 
              data = td.fg)
fotor3 <-glmer(Fotor ~  otherPast + frg.left+ frg.cv+  (1|Org),
              family = binomial, 
              data = td.fg)
fotor4 <-glmer(Fotor ~  otherPast + Rule +  cogSC1 + frg.cv+  (1|Org), 
               family = binomial, 
               data = td.fg)
fotor5 <-glmer(Fotor ~  otherPast + Rule +  cogSC1 +  (1|Org), 
               family = binomial, 
               data = td.fg)
tab_model(fotor, fotor1, fotor2, fotor3, fotor4, fotor5, show.aic = TRUE)

# BEST OF FALL AND WINTER
tab_model(fotor3, wofg1, show.aic = TRUE)
```




# old OTOR models
Before including forage use.

TO: Examine w Fall Otor
    Explore impact of social network strength--impact of network ouside the soum

First determining the correct random effect term:
```{r}
wotor1 <- glmer(Wotor ~ hhTenureWPast + otherPast + Rule +  cogSC1 +   (1|Org), family = binomial, data = td) 

wotor2 <- glmer(Wotor ~ hhTenureWPast + otherPast + Rule +  cogSC1 +   (1|Soum), family = binomial, data = td) 

tab_model(wotor1, wotor2)
plot_models(wotor1, wotor2)

tab_model(wotor1, show.aic = TRUE, show.icc= TRUE, rm.terms = "Rule.Q", 
          title = "Winter Otor",
          pred.labels = c("Intercept", 
                          "Tenure: Wtr Pasture", 
                          "Access to Other Pastures", 
                          "Rule formality", 
                          #"Rule-quadratic", 
                          "Cognitive SC"))

```
The Conditional R^2 and the AIC support RE for Org over Soum.

Inclusion of diff terms:
    NEED TO TRY W CBRM? No, bc redundant w Org
  WINTER OTOR
```{r}
wotor1 <- glmer(Wotor ~ hhTenureWPast + otherPast + Rule +  cogSC1 +   (1|Org), family = binomial, data = td.sc)


wotor2 <- glmer(Wotor ~ hhTenureWPast + otherPast + Rule +  bondSC +   (1|Org), family = binomial, data = td.sc)

wotor3 <- glmer(Wotor ~  otherPast + Rule + hhTenureWPast+  (1|Org), family = binomial, data = td)
  # w just Tenure not Rules
wotor4 <- glmer(Wotor ~  otherPast + hhTenureWPast+ (1|Org), family = binomial, data = td)
  # w just Rule not Tenure
wotor5 <-glmer(Wotor ~  otherPast + Rule+ (1|Org), family = binomial, data = td)

  # w Just access to other pastures:
wotor6 <-glmer(Wotor ~  otherPast + (1|Org), family = binomial, data = td)

#anova(wotor1, wotor3, wotor4, wotor5, wotor6)

tab_model(wotor3, wotor4, wotor5, wotor6, show.aic = TRUE, show.icc = FALSE)

```

  FALL OTOR
  (more suport for Org as RE than Soum)
```{r}
fotor1 <- glmer(Fotor ~  otherPast + Rule +  cogSC1 + hhTenureWPast +  (1|Org), family = binomial, data = td.sc)
  # structSC
# fotor2 <- glmer(Fotor ~ hhTenureWPast + otherPast + Rule +  strSC2+  (1|Org), family = binomial, data = td.sc)
  # with just the bondingSC:
fotor2 <- glmer(Fotor ~ hhTenureWPast + otherPast + Rule +  bondSC+  (1|Org), family = binomial, data = td)

fotor3 <- glmer(Fotor ~  otherPast + Rule +  cogSC1 +  (1|Org), family = binomial, data = td)
#tab_model(fotor1, fotor2,fotor3, show.aic = TRUE)

fotor4<- glmer(Fotor ~  otherPast + Rule +    (1|Org), family = binomial, data = td)
tab_model(fotor1, fotor2,fotor3, fotor4, show.aic = TRUE)


#anova(fotor1, fotor3, fotor4, fotor5, fotor6)

tab_model(fotor3, fotor4, fotor5, fotor6, wshow.aic = TRUE, show.icc = FALSE)



plot_model(bestSp,
           title = "Reserve Spring Pastures", 
           sort.est = TRUE,
           #auto.label = FALSE, 
           axis.labels = c("Rules","cbrmYN","Camp Tenure", "Social Capital", "Pasture Tenure"),
           colors = "blue") 


tab_model(fotor1, show.aic = TRUE, show.icc= TRUE, rm.terms = "Rule.Q", 
          title = "Fall Otor",
          pred.labels = c("Intercept", 
                          "Tenure: Wtr Pasture", 
                          "Access to Other Pastures", 
                          "Rule formality", 
                          "Rule-quadratic", 
                          "Cognitive SC"))

```

  

# GETTING PREDICTED DATA:
```{r}
# haven't figured out how to do this with the RE included so have to redo w/o
wot<- glm(Wotor ~  otherPast + frg.left + Rule + cogSC1, family = binomial, data = td.fg)


# start w just one value for each
wo_dat <- cbind(expand.grid(otherPast=c(1,2,3),
                            Rule=c(0,1,2), 
                            hhTenureWPast= c(0,1), 
                            hhTenureWCamp = c(0,1), 
                            cogSC1=seq(0,2, 0.1), 
                            frg.left = seq(0,100,1),
                            frg.cv = seq(0,50,1)
                            ))
wo_dat %<>% mutate_at(c(1:2), funs(ordered(.)))
wo_dat %<>% mutate_at(3:4, funs(factor(.)))

#predict
woPred<- predict(wot, wo_dat, type="response")
wopredDat <- data.frame(wo_dat, woPred)

ggplot(wopredDat, aes(x= frg.left, y=(woPred*100), color = Rule)) +
   #geom_smooth()+
   geom_smooth(position=position_jitter(width=0.1,height=0.1))+
   coord_cartesian(xlim = c(0,100))+
   xlab("frg.left")+
   ylab("predicted prob of winter otor") +
   facet_grid(.~otherPast, labeller = label_both)

ggplot(wopredDat, aes(x= cogSC1, y=woPred, color = Rule)) +
   #geom_smooth()+
   geom_smooth(position=position_jitter(width=0,height=.001))+
   coord_cartesian(xlim = c(0,2))+
   xlab("cognitive social capital")+
   ylab("predicted prob of winter otor") +
   facet_grid(.~otherPast, labeller = label_both)


# w forage available:
ggplot(wofupredDat, aes(x= frg.avg, y=wofuPred, color= Rule)) +
#geom_smooth()+
geom_smooth(position=position_jitter(width=.001,height=.001))+
coord_cartesian(xlim = c(0,100))+
xlab("forage use")+
ylab("predicted prob of winter otor") +
facet_grid(.~otherPast, labeller = label_both)


```
Fall Otor Predicted

```{r}
# haven't figured out how to do this with the RE included so have to redo w/o
fot<- glm(Fotor ~  otherPast + Rule + hhTenureWPast + cogSC1, family = binomial, data = td)

fotorgm <-glm(Fotor ~  otherPast + Rule +  cogSC1 + frg.cv, family = binomial, data = td.fg)

fotorav <-glm(Fotor ~  otherPast +   cogSC1 + frg.left + frg.cv, family = binomial, data = td.fg)

# start w just one value for each
fo_dat <- cbind(expand.grid(otherPast=c(1,2,3),
                            Rule=c(0,1,2), 
                            #hhTenureWPast= c(0,1), 
                            cogSC1=seq(0,2, 0.25),
                            frg.cv=seq(0,100,1)
                            ))

fo_dat %<>% mutate_at(c(1:2), funs(ordered(.)))
#fo_dat %<>% mutate_at(3, funs(factor(.)))


#predict(finalW, p_dat, type="response")
foPred<- predict(fotorgm, fo_dat, type="response")
fopredDat <- data.frame(fo_dat, foPred)

foPredav<- predict(fotorav, fo_dat_av, type="response")
fopredDatav <- data.frame(fo_dat_av, foPredav)

```

Then plot the predicted data:
```{r}

plot(woPred~otherPast, data= wopredDat)

  #FALL OTOR:
ggplot(fopredDat, aes(x= frg.cv, y=foPred, color= Rule)) +
  geom_smooth()+  
  #geom_smooth(position=position_jitter(width=.01,height=.01))+
  coord_cartesian(xlim = c(0,100))+
  xlab("% forage remaining")+
  ylab("predicted prob of fall otor") +
  facet_grid(.~otherPast, labeller = label_both)

# w model that includes frg.avg in addition to frg.cv
## yields approx the same plot
ggplot(fopredDatav, aes(x= frg.cv, y=foPredav, color= Rule)) +
  geom_smooth()+  
  #geom_smooth(position=position_jitter(width=.01,height=.01))+
  coord_cartesian(xlim = c(0,100))+
  xlab("CV forage use")+
  ylab("predicted prob of fall otor") +
  facet_grid(.~otherPast, labeller = label_both)

ggplot(fopredDat, aes(x= cogSC1, y=foPred, color= Rule)) +
  geom_smooth()+  
  #geom_smooth(position=position_jitter(width=.01,height=.01))+
  coord_cartesian(xlim = c(0,2))+
  xlab("cognitive social capital")+
  ylab("predicted prob of fall otor") +
  facet_grid(.~otherPast, labeller = label_both)
```

```{r}
ggplot(td.fg, aes(x= frg.avg, y = frg.cv, color = ez)) + 
  geom_point() +
  xlab("Percent Forage Use")+
  ylab("LT CV of % Forage Use")
  
```

