---
title: "Tenure, Rules and Practices..."
output:
  html_document:
    df_print: paged
  pdf_document: default
---
```{r setup, echo = FALSE, message = FALSE, include = FALSE, warning= FALSE}
library(foreign)
#library(corrplot)

library(magrittr)
library(tidyr)
library(dplyr)
library(ggplot2)
#library(rgdal)
#library(sp)
library(readxl)
library(knitr)
library(summarytools)
library(lme4)
```

## SO WHAT DO WE HAVE SO FAR?
1. Not a super strong relationship between Rules (on timing of grazing) and Cognitive Social Capital, but need to spend some more time on this. But there is a diff in this relationship across diff ecological zones (as we predicted). This is just prelim, need to look at this some more.
2. Probability of Reserving Winter Pastures is explained more by Tenure (Rights to the Pasture) than Rule Formality (regarding Timing of Grazing)

## NOTES ON THINGS I STILL NEED TO INVESTIGATE:
1. Tenure on Winter Campsite 
    17 Sept : started incorporating this var, and get similar results, and even better if use both
              see approx lines: 
2. Compare results for a diff response variable: Practice of Reserving Spring Pastures
    17 Sept : just got those vars added to the df, still need to test. 
3. Other potential practices: Hay Cutting, Well Use
4. Random/varying intercept vs. slope models... what covariates may impact slope vs. grouping vars that impact intercept
     17 Sept : DO we need to control for Org? add as a random intercept or slope?? need to think about this. 
     
     
## when I come back: 
- summarize results so far and send to Maria
-

```{r, warning= FALSE, message = FALSE, echo = FALSE, results = "hide"}
# THIS IS THE FULL DATASET WITH ALL 700
  # the org level data are merged in to this as well. 
mor2FULL<- foreign::read.spss("./data/Org_HHS_May2016_5_28_16.sav" , 
                 to.data.frame=TRUE,
                 use.value.labels=FALSE) #
# tidy format
tbl_df(mor2FULL)

# This is JUST the HHS, not the combined one above, so it doesn't have the Org Level Variables in it:
sc<- foreign::read.spss("./data/HHSAnal_April23.sav" , 
                 to.data.frame=TRUE,
                 use.value.labels=FALSE) 
tbl_df(sc)


td<- mor2FULL%>% dplyr::select(
                      # Response Variables (Practices)
                  ResWint = a_ResWint,  # Reserve Winter Pastures
                  ResSpr = b_ResSpr,    # Reserve Spring Pastures
                      # Predictor Variables 
                    # org-level Tenure q:
                  TenureWPast = q02a_RightNatWintPast,   # Tenure Rights on Winter Pasture (Inf/ use contract/possession contract)                                                                                           #  But only 2 factors in answersinf & use? 
                  TenureSpPast =q02a_RightNatSpringPast, # Tenure rights on Spring Pasture
                    # hh-level tenure q:
                  UseWPast = A_UsWtrPast,                # have or use winter pasture -- 2/3 yes, 1/3 no
                  UseWCamp    = A_UsWtrCamp,             # have or use a winter Campsite
                  UseSpPast = A_UsSepSprPas,             # have or use a separate spring pasture
                  ContractSpPast = B_ContractSprPast,    # use or possession contract for spring pasture
                  ContractWPast= B_ContractWtrPast,      # use or possession contract for winter pasture -- most are no
                  ContractWCamp = B_ContractWtrCamp,     # have a use or possession contract for the winter camp
                    #org-level Rules Q
                  Rule = q03_TimingRules3.3,       # Rule formality 
                  ez = Ecologicalzone_4,           # ez 
                  Trsp = AnotherAilLSOnPast,
                  cbrmType = CBRM_type,
                  cbrmYN = CBRM_Y_N,
                  cogSC1 = CognSC,                 # mean of scores for items included, scaled 0-2 
                  cogSC2 = CognSC2,                # sum of scores, 0-12
                  #cogSCAgg = CognSC_Agg           # NOT SURE HOW THIS WAS CALC'D, range is 0.41 - 2
                  RefNum = SurveyRefNumber,
                  Org = ORG_CODE
                  )
td %<>% mutate_at(c(5:7,12:15), funs(factor(.)))
td %<>% mutate_at(c(3:4,8:11), funs(ordered(.)))
# should we make TenurePast ordered also????

```

## Add Recoded Winter Camp Tenure. 
First tried to recode the Winter Camp data using 2 diff vars, so that it was No-don't use, Yes-use but don't have a contract or Yes-use and do have a use or poassession contract. None of that was helping to explain, maybe bc so many Use, but the spread is a little more vaired for just the contracts question. 
```{r}
  # the first way tha ti did it, using both variables:
# td<- mutate(td, WtrCamp = case_when(UseCamp == 0 & TenureCamp == 0 ~ 0,   # No use or contract
#                                     UseCamp == 1 & TenureCamp == 0 ~ 1,   # Yes use, no contract
#                             UseCamp == 1 & TenureCamp == 1 | TenureCamp == 2 ~ 2, # Yes use, yes contract
#                             TRUE ~ NA_real_))                                 # else NA
# td %<>% mutate_at(13, funs(ordered(.)))

td<- mutate(td, TenureWCamp = case_when(ContractWCamp == 0|ContractWCamp == 3 | ContractWCamp == 4 ~ 0,   # No contract
                                       ContractWCamp == 1 ~ 1,   # Yes use contract
                                       ContractWCamp == 2 ~ 2,   # Yes possession contract
                                       TRUE ~ NA_real_))                                 # else NA
#td %<>% mutate_at(14, funs(ordered(.)))


  # This method makes dummy variables:
# td.mut<- mutate(td, r1_No = ifelse(r1 == 0, 1, 0))
# raw.data<- mutate(raw.data, r1_Inf = ifelse(r1 == 1, 1, 0))
# raw.data<- mutate(raw.data, r1_Form = ifelse(r1 == 2, 1, 0))
# raw.data %<>% na.omit()

```

Summarize data for this analysis:
 Almost everyone said that they use a winter campsite, and around 2/3 of those hh have a use or possession contract. Only one hh said they have rights but do not use it (reliable?) so maybe we can just use the contract Q, and not worry about also using the Use Q?
```{r}
sumdf<- dfSummary(td)
sumdf

# 3-Way Frequency Table
mytable <- xtabs(~A_UsWtrCamp+B_ContractWtrCamp, data=mor2FULL)
ftable(mytable) # print table 

ftable(td.mut$WtrCamp, td.mut$TenurePast)
```

First some data exploration plots:
Plot 1: ResWint Pasture ~ Tenure & CBRM_YN
Plot 2: cog soc cap ~ Rules & ez
Is this second plot indicating the highest Cogn Social capital in Desert Steppe w/ No Rules? 
Plot 3: ResWint Pasture ~ WtrCamp & CBRM_YN
```{r, echo = FALSE, message = FALSE, warning= FALSE}
#library(ggplot2)
dens<- ggplot(td, aes(x = ResWint)) + geom_density() + facet_wrap(Tenure ~ cbrmYN)
dens  # 0/1 = cbrm no/yes and 1/2 = Right to Wint Pasture no/yes

ezlabels <- c("1"= "Desert Steppe", "2" = "Steppe", "3" = "Eastern Steppe", "4" = "Forest Mtn Steppe")
rulelabels <-c("0" = "None", "1"= "Informal", "2" = "Formal")
rsc<- ggplot(td, aes(x= cogSC1)) + 
        geom_density() + 
        facet_grid(Rule ~ ez, labeller=labeller(ez = ezlabels, Rule = rulelabels)) 
rsc

denscamp<- ggplot(td, aes(x = ResWint)) + geom_density() + facet_wrap(TenureWCamp ~ cbrmYN)
denscamp  # 0/1 = cbrm no/yes and 1/2 = Right to Wint Pasture no/yes

```
Rules vary by ecological zone 
```{r}
scaov<- kruskal.test(Rule ~ ez, data = td)
scaov

```
# TENURE + RULE FORMALITY
### varying INTERCEPT models:
As of now ez & cbrm not nested 

```{r, echo = FALSE, message = FALSE, include = FALSE, warning= FALSE}
        # this chunk is hidden. was exploring tenure & rules w/o EZ, but really doesn't make sense to not include it.
# tmod1<- glm(ResWint ~ Tenure, family = binomial("logit"), data = td)
# tmod2<- glm(ResWint ~ Tenure  + Rule, family = binomial("logit"), data = td)
# tmod3<- glm(ResWint ~ Tenure  * Rule, family = binomial("logit"), data = td)
# anova(tmod1, tmod2, tmod3)
```

## Tenure on Winter Pasture:
```{r, message = FALSE, warning= FALSE}
#Better to use lmer() for mixed effects ...
tm1 <- glmer(ResWint ~ TenureWPast + (1|ez), family = binomial,data = td)
tm2 <- glmer(ResWint ~ TenureWPast + (1|ez) + (1|cbrmType), family = binomial,data = td)
tm3 <- glmer(ResWint ~ TenureWPast + Rule + (1|ez), family = binomial,data = td)
tm4 <- glmer(ResWint ~ TenureWPast + Rule + (1|ez) + (1|cbrmType), family = binomial,data = td)
tm5 <- glmer(ResWint ~ TenureWPast + Rule + (ez|Rule), family = binomial,data = td)
tm6 <- glmer(ResWint ~ TenureWPast + Rule + cbrmYN + (1|ez) , family = binomial,data = td) # 2nd BEST SO FAR
tm7 <- glmer(ResWint ~ TenureWPast + cbrmYN + (1|ez) , family = binomial,data = td)   # BEST SO FAR
# How to tell if this is any better??? 
tm8 <- glmer(ResWint ~ TenureWPast + cbrmYN + (1|ez) + (cbrmYN|cbrmType), family = binomial,data = td) 

# OH BU TWE NEE DTO CONTROL FOR ORG, RIGHT?
# HOW BEST TO DO THIS??
tm9 <- glmer(ResWint ~ TenureWPast + cbrmYN + (1|ez) + (cbrmYN|Org), family = binomial,data = td)   #
```

Compare models: (looking at changes in loglikelihoods and deviance as add more complexity to model)
```{r,message = FALSE, warning= FALSE}
anova(tm1, tm2, tm3, tm4, tm5, tm6, tm7)

##Adding Rules does seem to improve a little, but not huge:

summary(tm2)
summary(tm3)
summary(tm3)
summary(tm4)
```
###But do we really get much from adding cbrm in here?
###Yes, if it is CBRM YN, not so if it's CBRM Type, but probably bc I am specifying it incorrectly... 


###Also: If look at coefficients, the intercepts vary only across cbrm type, not ez?
See coeffs for tm1,tm3 vs. tm2,4
```{r}
coefficients(tm1)
coefficients(tm2)
coefficients(tm3)
coefficients(tm4)
```

## Tenure on Winter Campsite:
**Q for MFG: There isn't a direct parallel Rules Q, but perhaps the timing Q still applies here?**
The best model from above was:
tm7 <- glmer(ResWint ~ TenurePast + cbrmYN + (1|ez) ) 

###NOTE: going from the recorded variable that included both Use and Contract on winter camp to the recoded var just using Contract on w camp does MUCH better at explaining Reserving Pastures.
```{r, message = FALSE, warning= FALSE}
#Better to use lmer() for mixed effects ...
cm1 <- glmer(ResWint ~ TenureWCamp + (1|ez), family = binomial,data = td)
cm2 <- glmer(ResWint ~ TenureWCamp + (1|ez) + (1|cbrmType), family = binomial,data = td)
cm3 <- glmer(ResWint ~ TenureWCamp + Rule + (1|ez), family = binomial,data = td)
# tm5 <- glmer(ResWint ~ TenureWCamp + Rule + (ez|Rule), family = binomial,data = td)

  # add tenure on pastures AND winter camp in one model: 
cm4 <- glm(ResWint ~ TenurePast + TenureWCamp, family = binomial,data = td)
  #  if check the chi sq on cm4 it is better than null, but not great
  #  1-pchisq(851.65-838.91, 617-614)
cm5 <- glm(ResWint ~ TenurePast + TenureWCamp + Rule , family = binomial,data = td)
cm6 <- glmer(ResWint ~ TenurePast + TenureWCamp + cbrmYN + (1|ez), family = binomial,data = td)
cm7 <- glmer(ResWint ~ TenurePast + TenureWCamp + Rule + cbrmYN + (1|ez), family = binomial,data = td)

```
The best model from above is: 
cm6 <- glmer(ResWint ~ TenurePast + TenureWCamp + cbrmYN + (1|ez), family = binomial,data = td)

And things don't improve if we add in Rule formality.



# Checking model assumptions, just to be safe
Assumption: The response y comes from a known distribution with a known mean-variance relationship
To check this assumption we look at a plot of residuals, and try to see if there is a fan shape.

Assumption: There is a straight line relationship between a known function g of the mean of y and the predictors x
To check this assumption, we check the residual plot above for non-linearity, or a U-shape. In our case there is no evidence of non-linearity. If the residuals seem to go down then up, or up then down, we may need to add a polynomial function of the predictors using the poly function.
```{r}
plot(cm2, which = 1)

# library(mvabund)
# cm.many <- manyglm(ResWint ~ WtrCamp + (1|ez), family="binomial", data=td)
# plot(cm.many)
```



#TENURE + CBRM
Exploring this relationship
As of 17 Sept this only includes the Tenure on Winter Pastures, and hasn't been fixed to use th enew variable name TenurePast
```{r}

tm6 <- glmer(ResWint ~ Tenure + (1|ez), family = binomial,data = td)
summary(tm6)
tm7 <- glmer(ResWint ~ Tenure + cbrmYN + (1|ez) , family = binomial,data = td) 
summary(tm7)
```
###So, including CBRM Y/N significantly improves model... but adding type as a grouping doesn't....
```{r}
tm8 <- glmer(ResWint ~ Tenure + cbrmYN + (1|ez) + (1|cbrmType), family = binomial, data = td)
#tm9 <- glmer(ResWint ~ Tenure + cbrmYN + cbrmType + (1|ez) , family = binomial, data = td)
anova(tm6, tm7, tm8)
```

###tm7 is signif imp over tm6....and we don't get improvement by adding cbrmType to this.....
#Here are the coefficients for this model (reminder: random intercept model)#
```{r}
coef(tm7)
```

What if we swap cbrmType for cbrmYN in tm7?
No big diff....
```{r}
tm10 <- glmer(ResWint ~ Tenure + cbrmType + (1|ez) , family = binomial,data = td)
anova(tm7, tm10)
```

# CBRM x RULES
Should we also look at the relationship between Practices, Rules and CBRM outside of Tenure?
... again rules are not signif, and nothign is unless you add is cbrmtn then that is signif
```{r}
# RULE + CBRM ?
tm11 <- glmer(ResWint ~ Rule +  cbrmYN + (1|ez) + (1|cbrmType), family = binomial,data = td)
summary(tm11) 
```

# SOCIAL CAPITAL & RULES ...
Given what we see above wrt the (weak) relationship between (this particular set of) Rules and (this one) Practice, does this mean for our hypothesizes relationships between Social Capital and the prevalance of Informal vs. Formal Rules? 
**Original Hypothesis:**
  Increased cognitive social capital will lead to more prevalence of *informal* rules [within certain ecological zones]
  Rules ~ SC + ez
### SC1 
```{r, message = FALSE, warning= FALSE}
library(MASS)
# need to use MASS::polr for ordered logistic regression
scm<- polr(Rule ~ cogSC1 , data = td, method = c("logistic"))
scm1<- polr(Rule ~ cogSC1 + ez, data = td, method = c("logistic"))

anova(scm, scm1) # big improvement by including ez, as we predicted
```
### SC2
```{r, message = FALSE, warning= FALSE}
# should compare w probit vs. logistic too....

sc2m<- polr(Rule ~ cogSC2 , data = td, method = c("logistic"))
summary(sc2m)
sc2m1<- polr(Rule ~ cogSC2 + ez, data = td, method = c("logistic"))
summary(sc2m1)
anova(sc2m, sc2m1) 
anova(scm1, sc2m1) # Social capital index 1 performs better
```
Social capital index 1 performs better but is very similar, so maybe depends on which will be easier to interpret


# RSV SPRING PASTURES 
New outcome variable : Reserve Spring Pastures
Do we see similar relationships with potential explanatory variables?

```{r}
# what other vars do we need to add to the dataframe? 
# 
sm1 <- glmer(ResSpr ~ TenureSpPast + cbrmYN + (1|ez), family = binomial,data = td)   #  SIGNIF!!! 


```

