---
output:
  html_document: default
  pdf_document: default
---
double check bc hhtenure wasnt set as factor in td

---
title: "Rules & Tenure Models"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
<Sept 9 2019>

TO DO:
- Set some global viz params to use for plots below.
-[Done 9-10-19]save all of the data import and wrangling to a separate script and export to an rdata file that we call back in here. 
-pull summary stats and cross-tabs to separate script.


```{r setup, echo = FALSE, message = FALSE, include = FALSE, warning= FALSE, cache= TRUE}
library(haven)  # this is the new package to use instead of (foreign)
#library(corrplot)
library(magrittr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(readxl)
library(knitr)
library(summarytools)
library(lme4)
library(sjPlot)
library(stringr)
library(kableExtra)
library(qwraps2)

options(scipen = 999)


# This is pulled from teh vignette for the summarytools pkg, which gives
# these suggested specifications to enable easy viewing of outputs:
# https://cran.r-project.org/web/packages/summarytools/vignettes/Introduction.html

opts_chunk$set(results = 'asis',      # This is essential (can also be set #at the chunk-level)
                comment = NA, 
                prompt = FALSE, 
                cache = FALSE, # additional global settings I want to have for this doc:
                message = FALSE,
                warning = FALSE)

st_options(plain.ascii = FALSE,        # This is very handy in all Rmd documents
            style = "rmarkdown",        # This too
            footnote = NA,             # Avoids footnotes which would clutter the results
            subtitle.emphasis = FALSE  # This is a setting to experiment with - according tothe theme used, it might improve the headings layout
           )   

```

```{r, echo=FALSE}
# this setting also also suggested from summarytools vignette:
st_css()                              # This is a must; without it, expect odd layout,
                                      # especially with dfSummary()
```


---- Data prep now located in 1_RTM-datapull.R: (hidden in report view)    
< not including Use params in the dataframe called td now >
That script does the following:
1. Everything is straight factors, num or chr except for Rules which is ordered.
2. Recodes household-level tenure vars:  
3. Per discussion on Jan 7 2018, have condensed use & possession responses in to one category. 
4. Adds dummy Vars for Rules : [this is only useful for a few of the models]
5. Creates a subset of the df that removes all records w/ NAs in Social capital

# Load Rdata files 
```{r}
load("./data/td.RData")
```


# MODELS:

In this doc I am only including the best models thus far. 
For full information on process of investigating alternate variable forms and model fits see Rules_model.Rmd

# 2. WINTER : 
Predicting Likelihood that a herder household will reserve Winter Pastures

We built {#} multilevel statistical models with different levels of complexity to model pasture managment behavior of herder households. In all models, the dependent variable was the binary variable of whether a household reserves Winter and Spring pastures. Model 1 is a random-intercept model without an explanatory variables. We included Organizational effects in the model as a random component; the assumption is that there is more similarity in the practices of a houshold within an organization that between organizations. In this model the variance iof the dependent variable is parsed in to household level variance and organization-level variance. 
*Eq. 1*: $y_{ij} = \gamma_{00} + U_{0j}$

where $y_i$ is the dependent variable measured at houhold $i$ in organization $j$. Model 1 was used as the baseline model to estimate the group-level variance in the dependent variable. We compared each model to an intercept-only model and models w random intercepts performed better in both instances.
We assessed subsets of the independent/predictor variables via a stepwise method to explore the relative model fits across different combinations of predictors.

### 2.1 Null Model 
Determining support for specifying random effect for Organization. 
[I am now unclear why we went with Org rather than Soum (or both), as Soum performs better below.
However, it may be because in the actual models everything worked better w Org not Soum]

The estimate of the constant is the logit of the proportion Reserving Pastures:
Testing null models w just the randon intercept specified, to see which of these accounts for the most var. 
None of these models are significant in and of themselves, acording to straight p-vals, but by examining the AIC/BIC across the models we can see that for the Winter Pastures there is variation across Soum and Org (more variation between than within) and  
for the Spring Pastures there is more var across only Soums, not Org.  
But no support for random intercepts by ecological zone (jives with results from other model runs).

[Based on these I am going to just go w Org as grouping var (random) for both w & sp]
```{r}
nullw  <-  glm ( ResWint ~ 1 , data=td, family=binomial)   # AIC = 977
nullw.r <-  glmer( ResWint ~ 1 + (1|Org), data=td, family=binomial) #AIC = 947.2
nullw.re <-  glmer( ResWint ~ 1 + (1|ez), data=td, family=binomial) #worse
nullw.rs <-  glmer( ResWint ~ 1 + (1|Soum), data=td, family=binomial) #better
nullw.rso <-  glmer( ResWint ~ 1 + (1|Soum) + (1|Org), data=td, family=binomial)  #best, AIC = 934.4
nullw.rsxo <-  glmer( ResWint ~ 1 + (Org|Soum), data=td, family=binomial)  
#anova(nullw.r, nullw.re, nullw.rs, nullw.rso, nullw.rsxo)
anova(nullw.r, nullw.rs, nullw.rso)

nulls  <-  glm ( ResSpr ~ 1 , data = td, family = binomial)
nulls.r <-  glmer( ResSpr ~ 1 + (1|Org), data = td, family = binomial) #better  AIC = 950
nulls.re <-  glmer( ResSpr ~ 1 + (1|ez), data = td, family = binomial) #worse
nulls.rs <-  glmer( ResSpr ~ 1 + (1|Soum), data = td, family = binomial) #better  (best, AIC = 913)
nulls.rso <-  glmer( ResSpr ~ 1 + (1|Soum)+ (1|Org), data = td, family = binomial)  # AIC = 915
#anova(nulls.r, nulls.re, nulls.rs, nulls.rso)
anova(nulls.r, nulls.rs, nulls.rso)

```


```{r}
summary(nullw.r )
summary(nulls.r )
```
Ref: http://data.princeton.edu/wws509/R/c3s1.html  


###2.2 Winter Pasture Tenure & Rule Formality
** Household level tenure var:**
This model uses the response from the Household-level survey regarding whether the hh has a Use or Possession contract for the Winter Pasture. Also incorporated the hh-level Q regarding tenure status on the Winter **CAMPSITE** as a predictor for these models as well.
Compared  multiple models in original work (Rules_model.Rmd) with different combinations of Rule vars, cbrm status and Social Capital param. 

Also, ended up specifying random intercept for Org when using the hh-level Tenure var.
Is this signif bc there is Org-level influence on either a) what kind of tenure a hh woudl have and/or b) how much they actually know about their tenure-status?
(note: much worse fit if include a random intercept for ez when using hh level tenure var. surprising that this doesn't vary?)

Reserving Winter Pastures ~ Tenure + cbrm + Rules + SocCap + (1 | Org)

*Now Rules are more significant than cbrm status.*

[Note jan8: added ordinal Rule para rather than the dummy var Rule/No]
Below I have just the results of a stepwise model comparison, based on all of the previous work re: the rel of these params.
Stepwise:  [Can only do this with model without random intercepts included, but generally the same message if we compare these manually, which I do in a diff doc]
In general I don't want to use this, as it is not theory based, just throwing it all in, but we did lots of testing prior and this was just to check. 
```{r}
fullmod <- glm(ResWint ~ hhTenureWCamp+hhTenureWPast +  Rule + RuleNo+ cbrmYN +cogSC1 +ez , family = binomial,data = td) 
backward <- step(fullmod)
summary(backward) #gives the best model
```

####Takeaway: The data are best explained by a model that includes:  
**Tenure on Winter Pasture AND Camp, Rule formality and cognitive social capital.**

BUT this form will not let us take random effects of Organization and/or Soum in to account, and we know from previous steps (see Rules_model.Rmd doc) that model fit improves with including random effect of Org, based on assumption that there may be more sim within group that among.  

So, this is the same model as above, but w random effects of Org specified. Modelling with BOTH winter tenure parameters :
Various attempts at models w ecological zone included as either fixed or random effect were not signif and/or performed poorly. Only ez3=Eastern Steppe was ever signif.

```{r}
# 
#htm7 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = td.sc)

htm7 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule +  cogSC1 +   (1|Org) , family = binomial, data = td.sc)
summary(htm7)

tab_model(htm7)
```
```{r}
wchi.diff<- (943.16-634.54)
wdf.diff<- (703-508)
pchisq(wchi.diff, wdf.diff, lower.tail = F)
```



**Can also look at the outputs as odds ratios:** which I find slightly easier to interpret.  
Based on htm7:

But, the Marginal R^2 is very low....
```{r}
tab_model(htm7)
```


The odds of a hh reserving winter pasture are lower if there are not Rules in place regarding timing of grazing of (winter pasture). 
However, the odds of the hh reserving pasture increase with increasing tenure on the winter camp. 
The odds of the household reserving pasture increases the most with increases in Social Capital.  
The conditional R2 describes the proportion of variance explained by both the fixed and random factors
morginal is just fixed factors.

But, while we can run the full models w random effect by Org specified and extract those coeffs (see above work) that **doesn't get us differences by ez which might be important,** and the models won't run w random effect by ez also included (won't converge)[this may be bc of issues revealed in the Steppe-only model  below?]
[Seeking help on this from another person]

So, maybe we look at these separately then. 
-either by ecological zone separately to see if diff models needed for diff zones. 
AND/or
-to assess the relative impacts of Rules across the zones. 

In the meantime, here's the original and predicted values. 
To visualize will have to decide a cut-off point for the fitted to assign 0/1
```{r}
df.htm7<- htm7@frame
wDat <- data.frame(htm7@frame, resid=residuals(htm7,type="pearson"),fitted=fitted(htm7))

theme= theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             panel.background = element_blank(),
             axis.text.y = element_blank(),
             axis.ticks = element_blank(),
             axis.line.x = element_line(color = "black"),
             axis.line.y = element_line(color = "black"),
             text = element_text(size = 20),
             legend.key = element_blank())
hist <- ggplot(wDat, aes(fitted, color = ResWint, fill = ResWint))
hist +
  theme +
  geom_dotplot(binwidth = 0.01, position = "jitter")+
  coord_cartesian(xlim = c(0,1))+
  xlab("Predicted value")+
  ylab(" ")+
  scale_color_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Winter Pastures")+
  scale_fill_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Winter Pastures")+
  geom_vline(xintercept = c(0.5), linetype = "dotdash", size = 1)

```

Let's explore the values w high predicted value but observed = 0 to see what's up. 
###Looks like there is a relationship between the level of social capital and the fitted value (pos). So operhaps the impact of SC1 is so great that the model is over prediction the probability that a hh will reserve pastures.###
```{r}
# filter the df of predicted vals it so it's the values on the right that were obsv No, pred Yes and look at summary stats:
wDat%>%dplyr::filter(fitted >= 0.5) %>% filter(ResWint == 0) %>% summary_table(.)
badpred <- wDat%>%dplyr::filter(fitted >= 0.5) %>% filter(ResWint == 0)
# let's compare those to the summary stats for the correctly predicted:
wDat%>%dplyr::filter(fitted >= 0.5) %>% filter(ResWint == 1) %>% summary_table(.)

# merge w the original data so can visualize by EZ:

#wDat.td<- left_join(wDat, td, by = "Org")


ggplot(wDat, aes(fitted))+geom_density()+facet_wrap(.~Rule)+theme_bw()

# histogram of predicted values, colored by Rule formality 
ggplot(wDat, aes(fitted, color= Rule)) + geom_density() 
ggplot(wDat, aes(fitted, color= hhTenureWPast)) + geom_density() 
ggplot(wDat, aes(fitted, color= hhTenureWCamp)) + geom_density() 
ggplot(wDat, aes(fitted, color= ResWint)) + geom_density() 
```


# 3. Reserve Spring Pastures**  

Do we see similar relationships with potential explanatory variables?  
nullSp<- glm( ResSpr ~1, data= td, family = binomial)  
This only works when we use the dummary variable version of the Rules var: RuleNo or RuleInf both work w basically same result. 
Again, not using the Org-level tenure var anymore.
```{r}
 ## Sp Pasture, household level tenure var:
htmSp <- glmer(ResSpr ~ hhTenureSpPast + cbrmYN + RuleNo + cogSC1 + (1|Org) , family = binomial, data = td ) # hmmmm.... now cbrm signif
summary(htmSp)

```

Double checking model fit with a stepwise procedure confirms (without the random effects) the significance of:  
**Household tenure on the Spring Pasture, *cbrm status* and cognitive social capital.** 
```{r}
fullSpmod <- glm(ResSpr ~ hhTenureSpPast+ hhTenureSpCamp+ Rule + RuleNo+ cbrmYN +cogSC1 , family = binomial,data = td.sc) 
backward <- step(fullSpmod)
summary(backward) #gives the best model
```

Best model as determined above, with the random effect of Org, presented as odds ratios:
```{r}
bestSp <- glmer(formula = ResSpr ~ hhTenureSpPast + hhTenureSpCamp+ cbrmYN + RuleNo+ cogSC1 + (1|Org), family = binomial, 
    data = td)
tab_model(bestSp)
```

**Interpretting the odds ratios:**  tenure on the spring pasture, membership in a formal CBRM and cognitive social capital all increase the odds that a household will reserve the spring pastures. Rules (re: timing of grazing) were not significant, but the coeffs indicate that the negative impact of NOT having rules on the odds of reserving pasture.. Conditional R2 describes the proportion of variance explained by both the fixed and random factors ... which, doesn't seem great?
In the meantime, here's the original and predicted values. 
To visualize will have to decide a cut-off point for the fitted to assign 0/1
```{r}
df.htmSp<- htmSp@frame
spDat <- data.frame(htmSp@frame, resid=residuals(htmSp,type="pearson"),fitted=fitted(htmSp))

theme= theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             panel.background = element_blank(),
             axis.text.y = element_blank(),
             axis.ticks = element_blank(),
             axis.line.x = element_line(color = "black"),
             axis.line.y = element_line(color = "black"),
             text = element_text(size = 20),
             legend.key = element_blank())
hist = ggplot(spDat, aes(fitted, color = ResSpr, fill = ResSpr))
hist +
  theme +
  geom_dotplot(binwidth = 0.01, position = "jitter")+
  coord_cartesian(xlim = c(0,1))+
  xlab("fitted value for probability reserve patures")+
  ylab(" ")+
  scale_color_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  scale_fill_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  geom_vline(xintercept = c(0.5), linetype = "dotdash", size = 1)


ggplot(spDat, aes(fitted, color= ResSpr)) + geom_density() +
  scale_color_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  scale_fill_manual(values = c("Maroon", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  geom_vline(data= filter(spDat, ResSpr == 1), aes(xintercept=median(fitted, na.rm=T)),  
               color="#2C3539", linetype="dashed", size=1)+
  geom_vline(data= filter(spDat, ResSpr == 0), aes(xintercept=median(fitted, na.rm=T)),  
               color="Maroon", linetype="dashed", size=1)+
  theme

```

```{r}

# histogram of predicted values, colored by Rule formality 
ggplot(spDat, aes(fitted, color= RuleNo)) + geom_density() 
ggplot(spDat, aes(fitted, color= hhTenureSpPast)) + geom_density() 
ggplot(spDat, aes(fitted, color= cbrmYN)) + geom_density() 



```





### SOCIAL CAPITAL & RULES ...  

Given what we see above wrt the (weak) relationship between (this particular set of) Rules and (this one) Practice, does this mean for our hypothesized relationships between Social Capital and the prevalance of Informal vs. Formal Rules? Does it vary by TYPE of pasture/season under consideration? Stronger relationship between rule formality and social capital for the Winter pastures compared to Spring pastures.

**Original Hypothesis:**  
  Increased cognitive social capital will lead to more prevalence of *informal* rules (within certain ecological zones)
  Rules ~ Social Capital + ecological zone
#### SC1 
```{r, message = FALSE, warning= FALSE}
library(MASS)
# need to use MASS::polr for ordered logistic regression
ezm<- polr(Rule ~ ez, data = td, method = c("logistic"))
scm<- polr(Rule ~ cogSC1 , data = td, method = c("logistic"))
scm1<- polr(Rule ~ cogSC1 + ez, data = td, method = c("logistic"))

anova(scm, scm1) # big improvement by including ez, as we predicted
summary(scm1) # outputs are re: prob of being in that class or lower
#intercepts are the zetas

fit.scm<- scm1$fitted.values
colnames(fit.scm)<- c("None", "Informal", "Formal")
scm.df<- data.frame(fit.scm, scm1$model)

```

Big improvement by including ez, as we predicted

# returns predicted class membership, so look for the highest estimated probability in each zone.
Edit this to create a table:
```{r}
# EZ = 1
predict(ezm, newdata = data.frame(ez="1"),type="p") #0 = No rules, Inf next
# EZ = 2
predict(ezm, newdata = data.frame(ez="2"),type="p") #1 = Inf, formal next
#EZ = 3
predict(ezm, newdata = data.frame(ez="3"),type="p") #1 = Inf, then no, then formal
#EZ = 4
predict(ezm, newdata = data.frame(ez="4"),type="p") #1 = Inf, then formal next


# calc cumulative probabilities of having certain rule formality:
exp(ezm$zeta - ezm$coefficients)/(1 + exp(ezm$zeta - ezm$coefficients))


#ggplot(scm.df, aes(x=)) 
```








**Separating out the data by ecological zone** 
to try to understand why having issues trying to incorporate ez:  
td by ez
```{r}
mfs <- td %>% filter(ez == 4)%>% drop_na()
ds  <- td.sc %>% filter(ez == 1)%>% drop_na()
st  <- td.sc %>% filter(ez == 2) %>% drop_na()

```
Now separate models for each ez

1st: Rules by EZ:
```{r}
# singular fit warning, but does yield diff coefficients for Rules by ez....
mtez<- glmer(ResWint ~ Rule + (1+ Rule|ez), family = binomial,data = td) 
coef(mtez)
```
Now separate models for each ez... based on the full models above:
htm7 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = td.sc)
htmSp <- glmer(ResSpr ~ hhTenureSpPast + cbrmYN + RuleNo + cogSC1 + (1|Org) , family = binomial, data = td ) 

**This isn't working out**  
So i'm hiding it for now.
None fitting? Intercept only models best for DS and ST?  
And social capital the only signif param in FMS? 
```{r, echo = FALSE, eval = FALSE}
mt.null <-  glm( ResWint ~ 1, data=mfs, family=binomial)
ds.null <-  glm( ResWint ~ 1, data=ds, family=binomial)
st.null <-  glm( ResWint ~ 1, data=st, family=binomial)

  # this model will not converge unless all of these parameters are included??
#mtm <- glmer(ResWint ~ TenureWPast + Rule + cbrmYN + cogSC1 + (1|Org) , data = mfs, family = "binomial")

mtmp <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = mfs)
stmp <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = st)
dsmp <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN+ cogSC1 +   (1|Org) , family = binomial, data = ds)


#dsmp <- glm(ResWint ~  hhTenureWPast+ hhTenureWCamp + Rule + cogSC1 , data = ds, family = "binomial")
dsfull <- glm(ResWint ~  hhTenureWPast+ hhTenureWCamp + cbrmYN+ Rule + cogSC1 , data = st, family = "binomial")
step(dsfull)
  # NONE OF THIS IS SIGNIF???
stfull <- glm(ResWint ~  hhTenureWPast+ hhTenureWCamp + cbrmYN+ RuleNo + cogSC1 , data = st, family = "binomial")
back<- step(stfull)

```


more histograms of params divided out by EZ:
```{r}
ggplot(ds, aes(cogSC1))+geom_density()+facet_grid(.~Rule)
ggplot(mfs, aes(cogSC1))+geom_density()+facet_grid(.~Rule)
ggplot(st, aes(cogSC1))+geom_density()+facet_grid(.~Rule)
ggplot(td, aes(cogSC1))+geom_density()+facet_wrap(.~Rule*ez)+theme_bw()

```



## ALSO NEED TO LOOK AT PREDICTED VALUES/DISTRIBUTIONS:
Our goal here is to calculate a predicted probability of Reserving Winter Pastures, for specific values of the predictors:
Tenure = 1
Rules = 1 vs. 2
cogSC1 continuous values….
To do that, create a dataframe w the specified values:
But we'll need to consider all combinations in order to really predict.

```{r}
finalW <- glm(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cogSC1, family = binomial, data = td)

# start w just one value for each
p_dat <- cbind(expand.grid(hhTenureWPast=c(0,1),hhTenureWCamp=c(0,1),Rule=c(0,1,2), cogSC1=seq(0,2, .25)))

p_dat %<>% mutate_at(c(1:2), funs(factor(.)))
p_dat %<>% mutate_at(3, funs(ordered(.)))





#predict(finalW, p_dat, type="response")
wPred<- predict(finalW, p_dat, type="response")

predDat <- data.frame(p_dat, wPred)


twp<- ggplot(predDat, aes(x= wPred, y=hhTenureWPast))+
  geom_dotplot(binaxis = "y", stackdir = "center")+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Winter Pasture ")
twp

twp<- ggplot(predDat, aes(x= wPred, color=hhTenureWPast))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Winter Pasture ")
twp

twc<- ggplot(predDat, aes(x= wPred, color=hhTenureWCamp))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Winter Camp ")

rf<- ggplot(predDat, aes(x= wPred, color=Rule))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Rule formality ")+
    #geom_vline(data= filter(predDat, Rule == 1), aes(xintercept=median(fitted, na.rm=T)),  
      #         color="#2C3539", linetype="dashed", size=1)+
  geom_vline(data= filter(predDat, Rule == 1), aes(xintercept=median(wPred, na.rm=T)) ,  
               color="#2C3539", linetype="dashed", size=1)+
  geom_vline(data= filter(predDat, Rule == 0), aes(xintercept=median(wPred, na.rm=T)),  
               color="Maroon", linetype="dashed", size=1)
rf
ggplot(predDat, aes(x= cogSC1, y= wPred, color = Rule))+
  geom_smooth()+
  coord_cartesian(xlim = c(0,2))+
  xlab("cognitive social capital")+
  ylab("predicted prob of reserving W pasture") #+
  #facet_wrap(.~hhTenureWPast)

ggplot(predDat, aes(x= wPred, y= hhTenureWPast, color = Rule))+
    geom_point(shape=1,position=position_jitter(width=.1,height=.1))

ggplot(predDat, aes(x= wPred, y= hhTenureWCamp, color = Rule))+
    geom_point(shape=1,position=position_jitter(width=.1,height=.1))

ggplot(td, aes(x= cogSC1, y= Rule))+
    geom_point(shape=1,position=position_jitter(width=.1,height=.1))+
    facet_wrap(.~ez)

```

Looking more at the predicted values:

```{r}
predDat%>%group_by(hhTenureWPast)%>%
  summarise(pred= median(wPred))

predDat%>%group_by(hhTenureWCamp)%>%
  summarise(pred= median(wPred))

predDat%>%group_by(Rule)%>%
  summarise(pred= median(wPred))


```


```{r}
finalS <- glm(ResSpr ~ hhTenureSpPast +cbrmYN + Rule + cogSC1, family = binomial, data = td)

# start w just one value for each
p_dat <- cbind(expand.grid(hhTenureSpPast=c(0,1),cbrmYN=c(0,1),Rule=c(0,1,2), cogSC1=seq(0,2, .25)))

p_dat %<>% mutate_at(c(1:2), funs(factor(.)))
p_dat %<>% mutate_at(3, funs(ordered(.)))





#predict(finalW, p_dat, type="response")
sPred<- predict(finalS, p_dat, type="response")

predDat <- data.frame(p_dat, sPred)


ggplot(predDat, aes(x= sPred, y=hhTenureSpPast))+
  geom_dotplot(binaxis = "y", stackdir = "center")+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Spring Pasture ")


ggplot(predDat, aes(x= sPred, color=hhTenureSpPast))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Spring Pasture ")


ggplot(predDat, aes(x= sPred, color=Rule))+
  geom_density()+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Rule formality ")

ggplot(predDat, aes(x= cogSC1, y= sPred, color = Rule))+
  geom_smooth()+  
  #geom_smooth(position=position_jitter(width=.01,height=.01))+
  coord_cartesian(xlim = c(0,2))+
  xlab("cognitive social capital")+
  ylab("predicted prob of reserving Sp pasture") #+
  #facet_wrap(.~hhTenureWPast)

ggplot(predDat, aes(x= sPred, y= hhTenureSpPast, color = Rule))+
    geom_point(shape=1,position=position_jitter(width=.1,height=.1))


```



NOT USEFUL YET
```{r, eval = FALSE}
theme= theme(panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(),
             panel.background = element_blank(),
             axis.text.y = element_blank(),
             axis.ticks = element_blank(),
             axis.line.x = element_line(color = "black"),
             axis.line.y = element_line(color = "black"),
             text = element_text(size = 20),
             legend.key = element_blank())
hist<- ggplot(predDat, aes(x= wPred, y= hhTenureWPast)) # color = ResWint, fill = ResWint))
hist +
  theme +
  #geom_dotplot(binwidth = 0.01, position = "jitter")+
  geom_dotplot(binaxis = "y")+
  coord_cartesian(xlim = c(0,1))+
  xlab("predicted value for probability reserve patures")+
  ylab("Tenure on Winter Pasture ")+
  scale_color_manual(values = c("DkBlue", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Spring Pastures")+
  scale_fill_manual(values = c("DkBlue", "#2C3539"), #change
                     labels = c("Do Not Reserve", "Reserve"),
                     name = "Winter Pastures")+
  geom_vline(xintercept = c(0.5), linetype = "dotdash", size = 1)




r.betas<- ggplot(mz.or, aes(x= ez, y = beta))+ 
  geom_point(size = 2)+
  theme+
   coord_cartesian(ylim = c(0,2))

kable(mz.or, format = "markdown")
```










# Create a new dataframe that includes population of people and livestock (as of now just aimag level #s, but woudl be interesting to look at soum level too)

```{r, eval = FALSE}
pop<- read.csv("./data/mor2data/2009Population.csv", header = TRUE)
# human population in thousands
# lsk population in thousands 

td$Aimag<- str_trim(td$Aimag, side = "both")

pop %<>% dplyr::select(-aimag)

#paused 
#td.a <- left_join(td, pop, by = c("Aimag"))
#td.a<- td.a %>% drop_na()
```



