KEEP THIS - it contains all of the models we considered.

---
title: "Tenure, Rules and Practices..."
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r setup, echo = FALSE, message = FALSE, include = FALSE, warning= FALSE}
library(foreign)
#library(corrplot)

library(magrittr)
library(tidyr)
library(dplyr)
library(ggplot2)
#library(rgdal)
#library(sp)
library(readxl)
library(knitr)
library(summarytools)
library(lme4)
```
9 Sept 2019:
NOTE: This is the full script with documentation of all of the candidate models that we explored. The best fit models were carried over to RuleModelsReport.Rmd in order to write up a summary for MFG. 


# [OLD, but keeping in case need to remember I thought of this as a thing to explore:] NEXT UP : making dummy vars for use and contract vars.


## SO WHAT DO WE HAVE SO FAR?

1. Probability of Reserving Winter Pastures is explained more by Tenure (Rights to the Pasture) than Rule Formality (regarding Timing of Grazing)
2. Not a super strong relationship between Rules (on timing of grazing) and Cognitive Social Capital, but need to spend some more time on this. But there is a diff in this relationship across diff ecological zones (as we predicted). This is just prelim, need to look at this some more.
## NOTES ON THINGS I STILL NEED TO INVESTIGATE:
1. Tenure on Winter Campsite 
    17 Sept : started incorporating this var, and get similar results, and even better if use both
              see approx lines: 
2. Compare results for a diff response variable: Practice of Reserving Spring Pastures
    17 Sept : just got those vars added to the df, still need to test. 
3. Other potential practices: Hay Cutting, Well Use
4. Random/varying intercept vs. slope models... what covariates may impact slope vs. grouping vars that impact intercept
     17 Sept : DO we need to control for Org? add as a random intercept or slope?? need to think about this. 
     
     
## when I come back: 
- summarize results so far and send to Maria
- 

```{r, warning= FALSE, message = FALSE, echo = FALSE, results = "hide"}
# THIS IS THE FULL DATASET WITH ALL 700
  # the org level data are merged in to this as well. 
mor2FULL<- foreign::read.spss("./data/Org_HHS_May2016_5_28_16.sav" , 
                 to.data.frame=TRUE,
                 use.value.labels=FALSE) #
# tidy format
tbl_df(mor2FULL)

# This is JUST the HHS, not the combined one above, so it doesn't have the Org Level Variables in it:
sc<- foreign::read.spss("./data/HHSAnal_April23.sav" , 
                 to.data.frame=TRUE,
                 use.value.labels=FALSE) 
tbl_df(sc)

  # subsetting the FULL (combined) dataset to a smaller df:
td<- mor2FULL%>% dplyr::select(
          #** Response Variables (Practices) ***
                  ResWint = a_ResWint,  # Reserve Winter Pastures
                  ResSpr = b_ResSpr,    # Reserve Spring Pastures
          #** Predictor Variables *** 
                  # Org-level Tenure q:
                  TenureWPast = q02a_RightNatWintPast,   # Tenure Rights on Winter Pasture
                                                         #(Inf/ use /possession contract)                                                             #But only 2 in Answ: Inf & Use 
                  TenureSpPast =q02a_RightNatSpringPast, # Tenure rights on Spring Pasture
                  # HH-level Tenure q:
                  UseWPast = A_UsWtrPast,                # Have or use Winter Pasture 
                                                          #  2/3 yes, 1/3 no
                  UseWCamp    = A_UsWtrCamp,             # Have or use a Winter Campsite
                  UseSpPast = A_UsSepSprPas,             # Have or use a sep Spring Pasture
                  ContractSpPast = B_ContractSprPast,    # Use/Poss contract for Sp Pasture
                  ContractWPast= B_ContractWtrPast,      # Use/poss contract for Wtr Pasture 
                                                            #  most are no
                  ContractWCamp = B_ContractWtrCamp,     # Use/Poss contract for Wtr Camp
                  #ORG-level Rules q:
                  Rule = q03_TimingRules3.3,       # Rule formality 
          #** Cognitive Social Capital :          
                    # see Ulambayar et al. (201?) for info on which Qs were used, how combined
                  cogSC1 = CognSC,                 # Mean of scores for items included
                                                      # scaled 0-2 
                  cogSC2 = CognSC2,                # Sum of scores, 0-12
                  #cogSCAgg = CognSC_Agg    # NOT SURE HOW THIS WAS CALC'D, range is 0.41 - 2
          #** confounding vars / fixed & random effects :
                  ez = Ecologicalzone_4,           # ez 
                  Trsp = AnotherAilLSOnPast,       # trespassing
                  cbrmType = CBRM_type,            # CBRM Type
                  cbrmYN = CBRM_Y_N,               # CBRM Yes/No
          
                  RefNum = SurveyRefNumber,
                  Org = ORG_CODE
                  )
td %<>% mutate_at(c(1:2,5:7,8:10,14:17), funs(factor(.)))
td %<>% mutate_at(c(3:4,11), funs(ordered(.)))
# should we make TenurePast ordered also????

```

## Add Recoded Winter Camp Tenure. 
First tried to recode the Winter Camp data using 2 diff vars (Use & Tenure), so that it was No-don't use, 
Yes-use but don't have a contract or 
Yes-use and do have a use or poassession contract. 
None of that was helping to explain, maybe bc so many Use, but the spread is a little more varied for just the contracts question. 
But now I'm not sure that we should use these, bc it doesn't capture any of the "don't know" answers, which were a lot and are not necesarily the same as No or NA.
Tried them once as Dummy Vars and that was not helpful. 
```{r}
  # the first way that i did it, using both variables:
# td<- mutate(td, WtrCamp = case_when(UseCamp == 0 & TenureCamp == 0 ~ 0,   # No use or contract
#                                     UseCamp == 1 & TenureCamp == 0 ~ 1,   # Yes use, no contract
#                             UseCamp == 1 & TenureCamp == 1 | TenureCamp == 2 ~ 2, # Yes use, yes contract
#                             TRUE ~ NA_real_))                                 # else NA
# td %<>% mutate_at(13, funs(ordered(.)))

 

# as of now we have set all of the "don't know"s to NAs? 
  # Winter Camp Tenure:
td<- mutate(td, hhTenureWCamp = case_when(ContractWCamp == 0 ~ 0,   # No contract
                                       ContractWCamp == 1 ~ 1,   # Yes use contract
                                       ContractWCamp == 2 ~ 2,   # Yes possession contract
                                       TRUE ~ NA_real_))         # else NA
   ##### DO WE NEED TO MAKE THESE ORDERED ....? #####
#td %<>% mutate_at(14, funs(ordered(.)))
  # Winter Pasture Tenure:
td<- mutate(td, hhTenureWPast = case_when(ContractWPast == 0 ~ 0,   # No contract
                                       ContractWPast == 1 ~ 1,   # Yes use contract
                                       ContractWPast == 2 ~ 2,   # Yes possession contract
                                       TRUE ~ NA_real_)) 
td<- mutate(td, hhTenureSpPast = case_when(ContractSpPast == 0 ~ 0,   # No contract
                                       ContractSpPast == 1 ~ 1,   # Yes use contract
                                       ContractSpPast == 2 ~ 2,   # Yes possession contract
                                       TRUE ~ NA_real_))         # else NA
   

td %<>% mutate_at(20:21, funs(ordered(.)))


  # This method makes dummy variables:
# td.mut<- mutate(td, r1_No = ifelse(r1 == 0, 1, 0))
# td.mut<- mutate(raw.data, r1_Inf = ifelse(r1 == 1, 1, 0))
# td.mut<- mutate(raw.data, r1_Form = ifelse(r1 == 2, 1, 0))
# raw.data<- mutate(raw.data, r1_Form = ifelse(r1 == 2, 1, 0))
# raw.data %<>% na.omit()

# Dummy Vars for Rules : 
td <- mutate(td, RuleNo = case_when(Rule == 0 ~ 1,   # No rules = 1
                                     Rule == 1 | Rule == 2 ~ 0,   # set others to zero
                                     TRUE ~ NA_real_))            # else NA

td <- mutate(td, RuleInf = case_when(Rule == 1 ~ 1,   # Informal rules = 1
                                     Rule == 0 | Rule == 2 ~ 0,   # set others to zero
                                    TRUE ~ NA_real_))            # else NA


td <- mutate(td, RuleFormal = case_when(Rule == 2 ~ 1,   # Formal rules = 1
                                     Rule == 0 | Rule == 1 ~ 0,   # set others to zero
                                     TRUE ~ NA_real_))            # else NA

td %<>% mutate_at(c(20:22), funs(factor(.)))
```

Another subset of the df that accounts for removal of NAs, so can compare across:
```{r}
td.sc <- td %>% drop_na(cogSC1)
```



Rules vary by ecological zone 
```{r}
scaov<- kruskal.test(Rule ~ ez, data = td)
scaov

```
# Null Model ------ 
steps Ref'd from http://data.princeton.edu/wws509/R/c3s1.html
the estimate of the constant is the logit of the proportion Reservign Pastures:
```{r}
null<-  glm( ResWint ~ 1, data=td, family=binomial)

nullSp<- glm( ResSpr ~1, data= td, family = binomial)
```

# TENURE + RULE FORMALITY
### varying INTERCEPT models:
As of now ez & cbrm not nested 


## Tenure on Winter Pasture:
 
 Note: this is using the Org-level Tenure Q... 
 
```{r, message = FALSE, warning= FALSE}
#Better to use lmer() for mixed effects ...
tm1 <- glmer(ResWint ~ TenureWPast + (1|ez), family = binomial,data = td)
tm2 <- glmer(ResWint ~ TenureWPast + (1|ez) + (1|cbrmType), family = binomial,data = td)
tm3 <- glmer(ResWint ~ TenureWPast + Rule + (1|ez), family = binomial,data = td)
tm4 <- glmer(ResWint ~ TenureWPast + Rule + (1|ez) + (1|cbrmType), family = binomial,data = td)
tm5 <- glmer(ResWint ~ TenureWPast + Rule + (ez|Rule), family = binomial,data = td)
tm6 <- glmer(ResWint ~ TenureWPast + Rule + cbrmYN + (1|ez) , family = binomial,data = td) # 2nd BEST SO FAR
tm7 <- glmer(ResWint ~ TenureWPast + cbrmYN + (1|ez) , family = binomial,data = td)   # BEST SO FAR

tm8 <- glmer(ResWint ~ TenureWPast + cbrmYN + (1|ez) + (1|Org), family = binomial,data = td)
tm8.1<- glmer(ResWint ~ TenureWPast + cbrmYN + (1|ez) + (1 + TenureWPast|Org), family = binomial,data = td)
# 

# Random intercept for ez and random slopes for effect of Rule and CBRM by ez : 
tmn <- glmer(ResWint ~ TenureWPast + (1+Rule|ez) + (1 + cbrmYN|ez),family = binomial,data = td)
tm9 <- glmer(ResWint ~ TenureWPast + Rule + cbrmYN + (1+ Rule|ez) + (1 + cbrmYN|ez), family = binomial,data = td) #
  #best one:
tm9.1 <- glmer(ResWint ~ TenureWPast  + cbrmYN + (1+ Rule|ez) + (1 + cbrmYN|ez), family = binomial,data = td) # best
tm9.2 <- glmer(ResWint ~ TenureWPast + Rule + (1+ Rule|ez) + (1 + cbrmYN|ez), family = binomial,data = td)
tm9.3 <- glmer(ResWint ~ TenureWPast  + cbrmYN + (1+ Rule|ez) + (1 + TenureWPast|ez), family = binomial,data = td)

tm9.4 <- glmer(ResWint ~ TenureWPast  + cbrmYN + (1+ Rule|ez) + (1|Org), family = binomial,data = td) # best
```

Compare models: (looking at changes in loglikelihoods and deviance as add more complexity to model)
Adding Rules doesn't seem to improve it 
```{r,message = FALSE, warning= FALSE}
anova(tm1, tm2, tm3, tm4, tm5, tm6, tm7)
anova(tmn, tm9, tm9.1, tm9.3)
anova(tm9, tm9.1, tm9.3)
```

[Note from Jan 10: not using Org-level param anymore and cbrm not signif when consider hh-level param]
## Tenure on Winter Campsite:
**Q for MFG: There isn't a direct parallel Rules Q, but perhaps the timing Q still applies here?**
The best model from above was:
tm7 <- glmer(ResWint ~ TenurePast + cbrmYN + (1|ez) ) 

###NOTE: going from the recorded variable that included both Use and Contract on winter camp to the recoded var just using Contract on w camp does MUCH better at explaining Reserving Pastures.
```{r, message = FALSE, warning= FALSE}
#Better to use lmer() for mixed effects ...
cm1 <- glmer(ResWint ~ hhTenureWCamp + (1|ez), family = binomial,data = td)
cm2 <- glmer(ResWint ~ hhTenureWCamp + cbrmYN+ (1|ez) , family = binomial,data = td) # BEST
cm3 <- glmer(ResWint ~ hhTenureWCamp + Rule + (1|ez), family = binomial,data = td)
# tm5 <- glmer(ResWint ~ TenureWCamp + Rule + (ez|Rule), family = binomial,data = td)

  # add tenure on pastures AND winter camp in one model: 
cm4 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + (1|ez), family = binomial,data = td)
  #  if check the chi sq on cm4 it is better than null, but not great
  #  1-pchisq(851.65-838.91, 617-614)
cm5 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + (1|ez), family = binomial,data = td)
cm6 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + cbrmYN + (1|ez), family = binomial,data = td)
cm7 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN + (1|ez), family = binomial,data = td)

# including random slopes : 
cm8 <- glmer(ResWint ~ TenureWPast + hhTenureWCamp  + (1+ Rule|ez) + (1 + cbrmYN|ez), family = binomial,data = td)

cm9 <- glmer(ResWint ~ TenureWPast + hhTenureWCamp + Rule + cbrmYN + (1+ Rule|ez) + (1 + cbrmYN|ez), family = binomial,data = td)

```
The best model from above is: 
cm6 <- glmer(ResWint ~ TenureWPast + TenureWCamp + cbrmYN + (1|ez), family = binomial,data = td)
# wait now that i've adjusted TenureWPast now Rules are more signif than cbrm?? Gah!
And things don't improve if we add in Rule formality.
[NOTE: Ported some of the above to down below to examine these nested models, but with Org as random intercept not ex, as other analyses showed that's better.]


# Checking model assumptions, just to be safe
Assumption: The response y comes from a known distribution with a known mean-variance relationship
To check this assumption we look at a plot of residuals, and try to see if there is a fan shape.

Assumption: There is a straight line relationship between a known function g of the mean of y and the predictors x
To check this assumption, we check the residual plot above for non-linearity, or a U-shape. In our case there is no evidence of non-linearity. If the residuals seem to go down then up, or up then down, we may need to add a polynomial function of the predictors using the poly function.
```{r}
plot(cm2, which = 1)

# library(mvabund)
# cm.many <- manyglm(ResWint ~ WtrCamp + (1|ez), family="binomial", data=td)
# plot(cm.many)
```

# SPRING 
# Reserve Spring Pastures 
New outcome variable : Reserve Spring Pastures
Do we see similar relationships with potential explanatory variables?

This only works when we use the dummary variable version of the Rules var: RuleNo

[as of Jan 10 these are out of date:]
```{r}
 ## Sp Pasture
  # hhSpTenure, Rules, cbrm & SC
htmSp <- glmer(ResSpr ~ hhTenureSpPast + cbrmYN + RuleNo + cogSC1 + (1|Org) , family = binomial, data = td ) # hmmmm.... now Rules signif not cgrm....

# this fails:
#htmSpo <- glmer(ResSpr ~ ContractSpPast + cbrmYN + Rule + cogSC1 + (1|Org) , family = binomial, data = td ) # hmmmm.... now Rules signif not cgrm....

#htmSp.1 <- glmer(ResSpr ~ TenureSpPast + cbrmYN + RuleNo + cogSC1 + (1|Org) , family = binomial, data = td ) # hmmmm.... now Rules signif not cgrm....

summary(htmSp)
#summary(htmSp.1)
```




#TENURE + CBRM
Exploring this relationship
As of 17 Sept this only includes the Tenure on Winter Pastures, and hasn't been fixed to use th enew variable name TenurePast
```{r}

t1 <- glmer(ResWint ~ hhTenureWPast + (1|ez), family = binomial,data = td)
summary(t1)
tc <- glmer(ResWint ~ hhTenureWPast + cbrmYN + (1|ez) , family = binomial,data = td) 
summary(tc)

t2  <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + (1|ez), family = binomial,data = td)
summary(t2 )

t2c <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + cbrmYN+ (1|ez), family = binomial,data = td)
summary(t2c)

tr <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + cbrmYN+ Rule + (1|ez), family = binomial,data = td)
summary(tr)
```
###So, including CBRM Y/N significantly improves model... but adding type as a grouping doesn't.... and once you add Rule cbrm is no longer signif---prob bc the Rule param is cor?
```{r}
#tm8 <- glmer(ResWint ~ Tenure + cbrmYN + (1|ez) + (1|cbrmType), family = binomial, data = td)
#tm9 <- glmer(ResWint ~ Tenure + cbrmYN + cbrmType + (1|ez) , family = binomial, data = td)
anova(tm6, tm7, tm8)
```

###tm7 is signif imp over tm6....and we don't get improvement by adding cbrmType to this.....
#Here are the coefficients for this model (reminder: random intercept model)#
And some contingency tables..... 
```{r}
coef(tm7)

cbctable<- xtabs(~cbrmYN+ hhTenureWCamp, data= td) # should we use org level or hh level data for this Q?
cbptable<- xtabs(~cbrmYN+ hhTenureWPast, data= td) # should we use org level or hh level data for this Q?

ftable(cbctable)
summary(cbctable)

ftable(cbptable)
summary(cbptable)

# recoding tenure to be no/yes to compare that....
wcNY<- mutate(td, hhTenureWCamp = case_when(ContractWCamp == 0|ContractWCamp == 3 | ContractWCamp == 4 ~ 0,   # No contract
                                       ContractWCamp == 1 | ContractWCamp == 2 ~ 1,   # Yes contract, either use or possession
                                       TRUE ~ NA_real_))                                 # else NA
#td %<>% mutate_at(14, funs(ordered(.)))
wpYN<- mutate(td, hhTenureWPast = case_when(ContractWPast == 0|ContractWPast == 3 | ContractWPast == 4 ~ 0,   # No contract
                                       ContractWPast == 1 | ContractWPast == 2 ~ 1,   # Yes  contract
                                       TRUE ~ NA_real_)) 

cbctable2<- xtabs(~cbrmYN+ hhTenureWCamp, data= wcNY) # should we use org level or hh level data for this Q?
cbptable2<- xtabs(~cbrmYN+ hhTenureWPast, data= wpYN) # should we use org level or hh level data for this Q?

ftable(cbctable2)
summary(cbctable2)

ftable(cbptable2)
summary(cbptable2)

```

What if we swap cbrmType for cbrmYN in tm7?
No big diff....
```{r}
tm10 <- glmer(ResWint ~ Tenure + cbrmType + (1|ez) , family = binomial,data = td)
anova(tm7, tm10)
```

# CBRM x RULES
Should we also look at the relationship between Practices, Rules and CBRM outside of Tenure?
... again rules are not signif, and nothign is unless you add in cbrmtn then that is signif
```{r}
# RULE + CBRM ?
tm11 <- glmer(ResWint ~ Rule +  cbrmYN + (1|ez) + (1|cbrmType), family = binomial,data = td)
summary(tm11) 
```

# SOCIAL CAPITAL & RULES ...
Given what we see above wrt the (weak) relationship between (this particular set of) Rules and (this one) Practice, does this mean for our hypothesized relationships between Social Capital and the prevalance of Informal vs. Formal Rules? 
**Original Hypothesis:**
  Increased cognitive social capital will lead to more prevalence of *informal* rules [within certain ecological zones]
  Rules ~ Social Capital + ecological zone
### SC1 
```{r, message = FALSE, warning= FALSE}
library(MASS)
# need to use MASS::polr for ordered logistic regression
scm<- polr(Rule ~ cogSC1 , data = td, method = c("logistic"))
scm1<- polr(Rule ~ cogSC1 + ez, data = td, method = c("logistic"))

anova(scm, scm1) # big improvement by including ez, as we predicted
```
### SC2
```{r, message = FALSE, warning= FALSE}
# should compare w probit vs. logistic too....

sc2m<- polr(Rule ~ cogSC2 , data = td, method = c("logistic"))
summary(sc2m)
sc2m1<- polr(Rule ~ cogSC2 + ez, data = td, method = c("logistic"))
summary(sc2m1)
anova(sc2m, sc2m1) 
anova(scm1, sc2m1) # Social capital index 1 performs better
```
Social capital index 1 performs better but is very similar, so maybe depends on which will be easier to interpret




```{r}
# what other vars do we need to add to the dataframe? 
# 
sm1 <- glmer(ResSpr ~ TenureSpPast + cbrmYN + (1|ez), family = binomial,data = td)   #  SIGNIF!!! 


```


Plotting the fixed and random effects 
library(devtools)
devtools::install_github("strengejacke/sjPlot")
package "effects" not found??
Per sjPlot doc: "the marginal R-squared considers only the variance of the fixed effects, while the conditional R-squared takes both the fixed and random effects into account.

Plotting model results, inc residual fits:
```{r}
plot(htm6)
plot(htm6, type = c("p", "smooth") , id = 0.05) # id outliers
plot(htm6, sqrt(abs(resid(.))) ~ fitted(.), type=c('p', 'smooth'))
plot(htm6, resid(.) ~ fitted(.), abline=c(h = 0),  lty = 1,  type = c("p", "smooth")) #


```
http://ddar.datavis.ca/pages/extra/titanic-glm-ex.pdf


td by ez
```{r}
mfs <- td %>% filter(ez == 4)
ds  <- td %>% filter(ez == 1)
st  <- td %>% filter(ez == 2)

```
Now separate models for each ez
```{r}
mt.null <-  glm( ResWint ~ 1, data=mfs, family=binomial)
ds.null <-  glm( ResWint ~ 1, data=ds, family=binomial)
st.null <-  glm( ResWint ~ 1, data=st, family=binomial)

  # this model will not converge unless all of these parameters are included??
#mtm <- glmer(ResWint ~ TenureWPast + Rule + cbrmYN + cogSC1 + (1|Org) , data = mfs, family = "binomial")


mtmp <- glm(ResWint ~  hhTenureWPast+  Rule + cbrmYN + cogSC1 , data = mfs, family = "binomial")
mtmc <- glm(ResWint ~  hhTenureWCamp+  Rule + cbrmYN + cogSC1 , data = mfs, family = "binomial")
mtm <- glm(ResWint ~  hhTenureWPast+ hhTenureWCamp+  Rule + cbrmYN + cogSC1 , data = mfs, family = "binomial")


dsmp <- glm(ResWint ~ hhTenureWPast + Rule + cbrmYN + cogSC1 , data = ds, family = "binomial")
dsmc <- glm(ResWint ~ hhTenureWCamp + Rule + cbrmYN + cogSC1 , data = ds, family = "binomial")


stmp <- glm(ResWint ~ hhTenureWPast + Rule + cbrmYN + cogSC1 , data = st, family = "binomial")

stmc <- glm(ResWint ~ hhTenureWCamp + Rule + cbrmYN + cogSC1 , data = st, family = "binomial")

anova(mt.null, mtm)
anova(ds.null, dsm)
anova(st.null, stm)

mtm <- glm(ResWint ~ TenureWPast + Rule + cbrmYN + cogSC1 , data = mfs, family = "binomial")
dsm <- glm(ResWint ~ TenureWPast + Rule + cbrmYN + cogSC1 , data = ds, family = "binomial")


```


Jan 8  insert: 
  Playing around w RuleNo dummary var vs. ordinal Rule and Org vs. ez random intercepts...
  original:
```{r}
htm5a <- glm(ResWint ~ hhTenureWPast + cbrmYN + RuleNo + cogSC1 , 
              family = binomial, data = td )
htm5 <- glmer(ResWint ~ hhTenureWPast + cbrmYN + RuleNo + cogSC1 + (1|Org), 
              family = binomial, data = td )
htm5.1 <- glmer(ResWint ~ hhTenureWPast + cbrmYN + Rule + cogSC1 + (1|Org), 
              family = binomial, data = td )
htm5.3 <- glmer(ResWint ~ hhTenureWPast + cbrmYN + RuleNo + cogSC1 + (1|ez), 
              family = binomial, data = td )
htm5.4 <- glmer(ResWint ~ hhTenureWPast + cbrmYN + Rule + cogSC1 + (1|ez), 
              family = binomial, data = td )
# none of my attempts to include random slopes (or intercepts) for ecological zone seem to be working...
htm5is <- glmer(ResWint ~ hhTenureWPast + Rule + cogSC1 + (1|Org) + (1 + Rule|ez), 
              family = binomial, data = td )

htm5b <- glmer(ResWint ~ hhTenureWPast +  RuleNo + cogSC1 + (1|Org), family = binomial, data = td )

tab_model(htm5, htm5.1, htm5.3, htm5.4)
```
htm5 and htm5.1 are best, but htm5 with the dummary var for Rules continues to perform the best.

RE-EXAMINING NESTED MODELS, based on what we've learned in other analyses:
```{r, message = FALSE, warning= FALSE}
  # pasture
cm1 <- glmer(ResWint ~ hhTenureWPast + (1|Org), family = binomial,data = td.sc)
cm2 <- glmer(ResWint ~ hhTenureWPast + cbrmYN+ (1|Org) , family = binomial,data = td.sc) # better
cm3 <- glmer(ResWint ~ hhTenureWPast + Rule + (1|Org), family = binomial,data = td.sc) # not better
cm4 <- glmer(ResWint ~ hhTenureWPast + cogSC1 + (1|Org), family = binomial,data = td.sc) # better
cm5 <- glmer(ResWint ~ hhTenureWPast + Rule + cogSC1 + (1|Org), family = binomial,data = td.sc) #BEST
cm6 <- glmer(ResWint ~ hhTenureWPast + Rule + cbrmYN +cogSC1 + (1|Org), family = binomial,data = td.sc)  
cm7 <- glmer(ResWint ~ hhTenureWPast + cbrmYN +cogSC1 + (1|Org), family = binomial,data = td.sc) #
```

# to look at the effect of rules by ecological zone
```{r}
  # 
mtez<- glmer(ResWint ~ hhTenureWPast + (1|ez), family = binomial,data = td) 
  # THIS YIELDS DIFF COEFFICIENTS FOR RULES BY EZ IN ADDITION TO DIFF INTERCEPTS BY EZ:
mtrez<- glmer(ResWint ~ hhTenureWPast + (1 + Rule|ez), family = binomial,data = td) 

coefficients(cmez)
```

--------code below here RETIRED:##---

cm4 <- glmer(ResWint ~ hhTenureWPast + cbrmYN + (1|Org) + (1 + Rule|ez), family = binomial,data = td) # nope

  # camp
cm1 <- glmer(ResWint ~ hhTenureWCamp + (1|Org), family = binomial,data = td)
cm2 <- glmer(ResWint ~ hhTenureWCamp + cbrmYN+ (1|Org) , family = binomial,data = td) # BEST
cm3 <- glmer(ResWint ~ hhTenureWCamp + Rule + (1|Org), family = binomial,data = td)
cm3 <- glmer(ResWint ~ hhTenureWCamp + Rule + (1|Org), family = binomial,data = td)
cm4 <- glmer(ResWint ~ hhTenureWCamp + cbrmYN + (1 + Rule|ez), family = binomial,data = td) #nope
cm4 <- glmer(ResWint ~ hhTenureWCamp + cbrmYN + (1|Org) + (1 + Rule|ez), family = binomial,data = td) # nope
  # add tenure on pastures AND winter camp in one model: 
cm4 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + (1|ez), family = binomial,data = td)
  #  if check the chi sq on cm4 it is better than null, but not great
  #  1-pchisq(851.65-838.91, 617-614)
cm5 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + (1|ez), family = binomial,data = td)
cm6 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + cbrmYN + (1|ez), family = binomial,data = td)
cm7 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cbrmYN + (1|ez), family = binomial,data = td)

# including random slopes : 
cm8 <- glmer(ResWint ~ TenureWPast + hhTenureWCamp  + (1+ Rule|ez) + (1 + cbrmYN|ez), family = binomial,data = td)

cm9 <- glmer(ResWint ~ TenureWPast + hhTenureWCamp + Rule + cbrmYN + (1+ Rule|ez) + (1 + cbrmYN|ez), family = binomial,data = td)
[old code above]


---Jan 10:
stepwise:Can only do this with model without random intercepts included, but generally the same message if we compare these manually
```{r}
fullmod <- glm(ResWint ~ hhTenureWCamp+hhTenureWPast +  Rule + RuleNo+ cbrmYN +cogSC1 , family = binomial,data = td.sc)  

backward <- step(fullmod)
summary(backward) #gives the best model
```



# So now to figure out how to get the coeffs of the best model by EZ: 

Get a "singular fit" warning if try to specify random effect by ez with the full model. This means it yields a single intercept value, rather than varying. But only if use WCamp or cogSC1. Which seems to indicate that ONLY WPasture & Rules interact w ez? But even still, in this formulation there is only a variable intercept specified. The coefficients for Rules or WPast don't vary. Does this indicate that we need to be specifying that the Rules and/or WPasture shoudl vary by ez? 
```{r}
# let's use this as an example:
cm5 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cogSC1 + (1|Org), family = binomial,data = td.sc) #BEST
summary(cm5)
  # this yields singular fit
#cm5 <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cogSC1 + (1|ez), family = binomial,data = td.sc) #BEST

cm5ez <- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cogSC1 + (1|Org) +  (1|ez) , family = binomial, data = td.sc)
  # this has variable intercept by ez but coeff of Rules is the same.
mtez<- glmer(ResWint ~ Rule + (1|ez), family = binomial,data = td) 
coefficients(mtez)
```


```{r}  
# singular fit warning, but does yield diff coefficients for Rules by ez....
mtez<- glmer(ResWint ~ Rule + (1+ Rule|ez), family = binomial,data = td) 
coef(mtez)
# but this yields a singular fit warning and yields same coeffs for intercept and all params. wtf.
mtez<- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp+ Rule + (1+ Rule|ez), family = binomial,data = td) 
coef(mtez)
  
  #  But now THIS yields diff intercepts AND diff coeffs for Rules by ez.
mtez<- glmer(ResWint ~ hhTenureWPast + Rule + (1+ Rule|ez), family = binomial,data = td) 
coef(mtez)

  # this will not converge:  
mtez<- glmer(ResWint ~ hhTenureWPast + hhTenureWCamp + (1+ Rule|ez), family = binomial,data = td) 

```

Generate a likelihood summary table:
```{r}
vcdExtra::LRstats(glmlist(titanic.glm1, titanic.glm2, titanic.glm3))
```

It can be useful to look at the distribution of the conditional models
```{r}
lattice::dotplot(ranef(htm7, which = "Org", condVar = TRUE), scales = list(y = list(alternating = 0)))
```

```{r}
lattice::dotplot(ranef(bestSp, which = "Org", condVar = TRUE), scales = list(y = list(alternating = 0)))
```

```{r}

popmod<- glm(ResWint ~ hhTenureWPast +hhTenureWCamp + Rule + cogSC1 + pop , family = binomial, data = td.a) 

back<- step(popmod)

```































Pseudor^2  Can't use this function w glmer object so removing random effects.
Get really low values, e.g. Nagelkirk is 0.094, when want the val to be at least .15 for a medium effect size....
But, not sure about using these for mixed effects models anyway.
```{r}
htm7.0<- glm(ResWint ~ hhTenureWPast + hhTenureWCamp + Rule + cogSC1  , family = binomial, data = td)
summary(htm7.0)
PseudoR2(htm7.0)
```